\section{Statement Bank}
\label{sec:statement-bank}

This bank fixes names for the informal mathematical obligations. The labels are
chosen so they can later become Lean-blueprint nodes.

\begin{definition}[Analytic genus]
\label{def:analytic-genus}
For a compact connected Riemann surface \(X\), define
\[
  g(X) := \dim_{\C} H^{0}(X,\Omega^{1}_{X}).
\]
\lean{JacobianChallenge.HolomorphicForms.analyticGenus}
\leanok
\proofplan
Instantiate finite-dimensionality of \(H^0(X,\Omega_X^1)\) from the Sec02 chain:
sup norm \(\to\) compact unit ball (Montel) \(\to\) Riesz theorem; then define
\(g(X)\) by `FiniteDimensional.finrank`.
\end{definition}

\begin{layman}
The \emph{analytic genus} of a compact Riemann surface is the complex
dimension of the space of global holomorphic 1-forms on it. The
previous section established that this dimension is finite, so it's an
honest natural number. By the genus-zero classification (next item),
this number also matches the topological genus — the count of handles
you'd see if you held the surface in your hands. The sphere has
analytic genus 0, the donut has 1, the two-handled pretzel has 2, and
so on. Why bother? Genus is the single most important invariant in
Riemann surface theory. The whole challenge revolves around tying the
analytic definition (vector-space dimension) to the topological one
(number of handles), and the bridge between them is forged by
Riemann–Roch.
\end{layman}

% Note: thm:fd-holomorphic-one-forms moved to
% tex/sections/02-holomorphic-forms-and-genus.tex (after
% input:finite-dimensionality), where it sits at the correct point in
% the sec02 finite-dim chain. The production-side discharger remains
% JacobianChallenge.HolomorphicForms.compactRiemannSurface_finiteDimensionalHolomorphicOneForms;
% the blueprint \lean{} now points at the Sec02 stub instead.

\begin{theorem}[Genus-zero classification]
\label{thm:genus-zero-classification}
\uses{input:riemann-roch,prop:genus-zero-degree-one-map,input:degree-one-isomorphism,def:analytic-genus,thm:analytic-eq-topological-genus}
For a compact connected Riemann surface \(X\),
\[
  g(X)=0 \quad\Longleftrightarrow\quad X \cong_{\mathrm{homeo}} \Sphere .
\]
\lean{genus_eq_zero_iff_homeo}
\leanok
\proofplan
\(\Rightarrow\): use Riemann--Roch at genus \(0\) to build degree-one meromorphic map
to \(\mathbf{P}^1\), then classify degree-one maps as homeomorphisms.
\(\Leftarrow\): compute holomorphic one-forms on the sphere as zero.
\end{theorem}

\begin{layman}
This is the first anti-hack theorem of the challenge: the analytic
genus of a compact Riemann surface is zero if and only if the surface
is homeomorphic to the topological sphere. Forward direction: genus
zero produces a degree-one meromorphic function, which is a
biholomorphism onto the Riemann sphere, which is homeomorphic to the
2-sphere. Reverse direction: a homeomorphism with the sphere makes
the topological genus zero, and the comparison theorem identifies
analytic and topological genus, giving analytic genus zero. Why
bother? It forbids the trivial fake construction
``\code{genus X := 0}.'' The genus has to actually equal the
topological genus — ruling out any constant function pretending to be
genus. Without this anchor, all the challenge's anti-hacks would be
wide open.
\end{layman}

\begin{definition}[Period pairing]
\label{def:period-pairing}
\uses{lem:period-homology-invariance,thm:period-pairing-from-path-integral}
The period pairing is the group homomorphism
\[
  \Pi_X : H_{1}(X,\Z) \longrightarrow \HdualX,\qquad
  \gamma \longmapsto \left(\omega \mapsto \int_{\gamma}\omega\right).
\]
\lean{JacobianChallenge.Periods.periodPairing}
\leanok
\proofplan
Define integration functional on cycles, prove path/homology invariance, and
package as an additive homomorphism into \(\HdualX\).
\end{definition}

\begin{layman}
The \emph{period pairing} bundles all the loop integrals at once. Take
any closed loop on the surface (a class in the integer homology — a
finite-rank free abelian group) and map it to the linear functional
``integrate any holomorphic 1-form along me.'' That gives an element
of the dual of the space of holomorphic 1-forms — an honest
finite-dimensional linear-algebraic gadget. The pairing sends loops to
such functionals, in a way that respects loop addition (concatenation)
and integer scaling. Why bother? It's the bridge from topology
(homology classes of loops) to analysis (linear functionals on
1-forms). The image of this map will be the period lattice, the
discrete grid that gets quotiented to form the Jacobian.
\end{layman}

\begin{theorem}[Period lattice theorem]
\label{thm:period-lattice}
\uses{input:riemann-bilinear,def:period-pairing,thm:analytic-eq-topological-genus}
The image \(\periods_X := \Pi_X(H_1(X,\Z))\) is a full lattice in the
real vector space underlying \(\HdualX\).
\lean{JacobianChallenge.Periods.periodFullComplexLattice}
\leanok
\proofplan
Apply Riemann bilinear relations to show full real rank and discreteness; combine
to obtain a full lattice in the underlying real vector space.
\end{theorem}

\begin{layman}
The image of the period pairing — the set of all integer-coefficient
combinations of period vectors — is a \emph{full lattice} inside the
real vector space underlying the dual of the holomorphic 1-forms.
``Full'' means it's a discrete grid spanning the whole real space, not
a sublattice of lower rank. This is a direct consequence of the linear
independence of the \(2g\) symplectic-basis period vectors (from the
Riemann bilinear relations), since \(2g\) independent vectors in a
\(2g\)-real-dimensional space generate a lattice of full rank. Why
bother? A full lattice is exactly the input the complex-torus package
needs to produce a compact quotient. With the period lattice in
hand, the Jacobian is just ``dual-of-1-forms modulo lattice'' — and
that quotient is automatically a compact complex Lie additive group.
\end{layman}

\begin{definition}[Analytic Jacobian]
\label{def:analytic-jacobian}
\uses{thm:period-lattice,prop:complex-torus-package,def:analytic-genus}
The Jacobian of \(X\) is the complex torus
\[
  \Jac(X) := \HdualX / \periods_X .
\]
\lean{Jacobian}
\leanok
\proofplan
Use period lattice theorem + complex torus quotient package to construct
\(\HdualX/\periods_X\) with additive, topological, and manifold structures.
\end{definition}

\begin{layman}
The \emph{Jacobian} of a compact Riemann surface is the quotient: take
the dual of the holomorphic 1-forms (a finite-dimensional complex
vector space), mod out by the period lattice (a full discrete grid),
and the result is a compact complex torus — a higher-dimensional
generalization of an ordinary donut. Why bother? This is the central
object of the challenge. Every theorem in the public API is about the
Jacobian or about maps into and out of it. The construction inherits
all the structural goodness of the complex-torus package — addition,
compactness, holomorphic atlas, Lie group structure — for free, just
by plugging in the dual space and the period lattice.
\end{layman}

\begin{definition}[Abel-Jacobi map]
\label{def:abel-jacobi}
\uses{def:analytic-jacobian,lem:aj-path-independence}
For \(P\in X\), define
\[
  \AJ_P(Q) :=
    \left[ \omega \mapsto \int_{P}^{Q}\omega \right] \in \Jac(X),
\]
where the path is arbitrary and the class is taken modulo periods.
\lean{Jacobian.ofCurve}
\leanok
\proofplan
Define by integrating forms from \(P\) to \(Q\); prove path-independence modulo
period lattice, then descend to Jacobian quotient class.
\end{definition}

\begin{layman}
Pick a base point on the surface. The \emph{Abel–Jacobi} map sends
any other point to the class in the Jacobian represented by ``integrate
every holomorphic 1-form along a path from base to here.'' Different
paths give answers differing by periods, but the period lattice is
exactly what the Jacobian quotients out, so the class doesn't depend
on which path you chose. The result is a holomorphic map from the
surface into its own Jacobian, sending the base point to zero. Why
bother? This is the central comparison map between the surface and
its Jacobian. It's holomorphic, and (crucially, on positive-genus
surfaces) it's injective — so the surface sits inside its Jacobian as a
genuine curve rather than collapsing to a point.
\end{layman}

\begin{theorem}[Abel-Jacobi theorem, point-separation form]
\label{thm:abel-jacobi-injective}
\uses{def:abel-jacobi,input:abel-theorem}
If \(g(X)>0\), then \(\AJ_P : X\to \Jac(X)\) is injective.
\lean{Jacobian.ofCurve_inj}
\leanok
\proofplan
Reduce equality of Jacobian classes to vanishing of all period functionals and
invoke Abel point-separation (Abel theorem input).
\end{theorem}

\begin{layman}
On a compact Riemann surface of positive genus, the Abel–Jacobi map is
\emph{injective}: distinct points on the surface go to distinct points
in the Jacobian. This is the second anti-hack theorem of the
challenge. The proof chain (worked out in detail in section 06):
equality of Abel–Jacobi images forces a principal divisor of the form
``one point minus another,'' which gives a degree-one map to the
Riemann sphere, which forces the surface to be the sphere — but the
sphere has genus zero, contradiction. Why bother? Injectivity rules
out trivial fake Jacobians like ``\code{Jacobian X := PUnit}''
(which would collapse all points to one) or any other construction
that fails to actually distinguish the surface's points. The genuine
compact-complex-Lie-group structure on the Jacobian, plus
point-separation, forces the construction to be honest.
\end{layman}

\begin{definition}[Degree and trace]
\label{def:degree-trace}
\uses{lem:pullback-forms,lem:trace-forms,def:branched-degree,thm:branched-degree-well-defined}
For a holomorphic map \(f:X\to Y\), define \(\deg(f)\) to be \(0\) if
\(f\) is constant and otherwise the topological degree of the associated
branched covering. For nonconstant \(f\), define the trace on one-forms
\[
  \tr_f : H^{0}(X,\Omega^{1}_{X}) \to H^{0}(Y,\Omega^{1}_{Y})
\]
by summing local inverse branches away from the branch locus and extending
holomorphically.
\lean{ContMDiff.degree, JacobianChallenge.TraceDegree.pullbackFormsLinearMap}
\leanok
\proofplan
Define degree by constant/nonconstant split; define trace by summing inverse
branches off branch locus and extending holomorphically across it.
\end{definition}

\begin{layman}
Two operations associated to a holomorphic map between compact Riemann
surfaces. The \emph{degree} counts how many times the map covers its
target — zero if the map is constant; otherwise the size of a generic
fiber, with multiplicities at branch points. The \emph{trace on
1-forms} is the natural way to push a holomorphic 1-form on the source
down to a holomorphic 1-form on the target, by summing over local
inverse branches and extending holomorphically across the branch
locus. Both are core ingredients of the push-pull machinery the
challenge demands. Why bother? Degree is the ``size'' of a
holomorphic map; trace is the natural pushforward operation on
1-forms. Together with pullback, they assemble into the trace
identity (next theorem), which forces the right interaction between
push, pull, and degree on Jacobians.
\end{layman}

\begin{theorem}[Trace-pullback identity]
\label{thm:trace-pullback}
\uses{def:degree-trace,lem:trace-forms,lem:pullback-forms}
For every \(\eta\in\HY\),
\[
  \tr_f(f^{*}\eta)=\deg(f)\,\eta.
\]
\lean{JacobianChallenge.TraceDegree.analyticPushforward_analyticPullback}
\leanok
\proofplan
Compute locally on regular values using inverse branches, then globalize by
analytic continuation to conclude \(\tr_f(f^*\eta)=\deg(f)\eta\).
\end{theorem}

\begin{layman}
Take a holomorphic 1-form on the target. Pull it back along the map
to get a 1-form on the source. Trace it back down to the target. The
result equals the original 1-form multiplied by the degree of the
map. The intuition: pulling back creates \(d\) copies of the form (one
per inverse branch in a generic fiber); summing them via the trace
recovers \(d\) times the original. Why bother? This is the algebraic
backbone of the fourth anti-hack theorem. After dualizing and
descending to Jacobians, it becomes ``push-then-pull equals
multiplication-by-degree'' on Jacobian elements — forcing push, pull,
and degree to interact through the classical trace identity rather
than through arbitrary homomorphisms invented to game the challenge.
\end{layman}

\begin{theorem}[Functoriality and holomorphicity of induced Jacobian maps]
\label{thm:push-pull-functoriality}
\uses{lem:push-pull-descend}
The maps \(f_{*}\) and \(f^{*}\) induced on Jacobians are holomorphic group
homomorphisms. They satisfy identity and composition laws:
\[
  (\mathrm{id})_*=\mathrm{id},\qquad (g\circ f)_*=g_*\circ f_*,
\]
\[
  (\mathrm{id})^{*}=\mathrm{id},\qquad (g\circ f)^{*}=f^{*}\circ g^{*}.
\]
\lean{Jacobian.pushforward_contMDiff, Jacobian.pushforward_id_apply, Jacobian.pushforward_comp_apply, Jacobian.pullback_contMDiff, Jacobian.pullback_id_apply, Jacobian.pullback_comp_apply}
\leanok
\proofplan
Construct descended maps from linear maps on \(\HdualX\), prove they preserve
period lattice, then establish holomorphicity and identity/composition laws.
\end{theorem}

\begin{layman}
The maps induced on Jacobians by holomorphic maps between Riemann
surfaces are well-behaved: they are holomorphic group homomorphisms,
they take the identity map of a surface to the identity map of its
Jacobian, and they compose correctly under composition of holomorphic
maps. The pullback reverses arrow direction (target to source); the
pushforward respects arrow direction (source to target). It's
``functoriality'' in the categorical sense: the assignment
``Riemann surface'' \(\mapsto\) ``Jacobian'' is a functor — both
contravariantly (via pullback) and covariantly (via pushforward).
Why bother? Without functoriality, the push-pull operations would be
ad-hoc and could be gamed; with it, they're forced to behave like
genuine geometric pushforwards and pullbacks. The challenge's API
requires this exact set of compatibility laws.
\end{layman}

\begin{theorem}[Pushforward-pullback identity]
\label{thm:pushforward-pullback}
\uses{thm:trace-pullback,lem:push-pull-descend}
For every \(P\in\Jac(Y)\),
\[
  f_{*}(f^{*}P)=\deg(f)\,P.
\]
\lean{Jacobian.pushforward_pullback}
\leanok
\proofplan
Descend the trace-pullback identity from one-forms to Jacobian quotient classes
and transport through the pushforward/pullback descent maps.
\end{theorem}

\begin{layman}
The fourth anti-hack theorem of the challenge. For any holomorphic
map between compact Riemann surfaces and any element of the target
Jacobian, applying pullback (to get an element of the source
Jacobian) and then pushforward (to get back to the target Jacobian)
recovers the original element multiplied by the degree of the map.
Combined with functoriality from the previous theorem, this forces
push, pull, and degree to interact through the classical trace
identity, no other interaction allowed. Why bother? This rules out
any fake construction that defines push and pull as arbitrary
unrelated homomorphisms. The genuine geometric pullback and
pushforward must satisfy this identity, so any implementation in Lean
has to actually compute the trace correctly. Together with the genus
classification, point separation, and torus structure, these four
anti-hack theorems make trivial fake Jacobians impossible.
\end{layman}
