\section{Compact Riemann Surfaces}
\label{sec:compact-riemann-surfaces}

\begin{layman}
A \emph{Riemann surface} is one of the most patient objects in
mathematics: a curved two-dimensional surface that, when you put a
microscope to any patch of it, looks like a piece of the complex
plane. The sphere is a Riemann surface --- every patch can be
described by a single complex coordinate \(z\). The doughnut surface
is a Riemann surface. Every smooth algebraic curve in the projective
plane, like the elliptic curve \(y^2 = x^3 + ax + b\), is a Riemann
surface. They are simultaneously geometric objects (something you
could mould out of clay) and analytic ones (you can do calculus on
them with complex numbers).

This section sets up the algebraic dictionary we'll need in every
later section. The first move is to ask: ``How does a function blow
up or vanish at a point?'' On the complex plane the answer is the
familiar \emph{order} of a Taylor expansion --- \(z^3\) vanishes to
order three at the origin, \(1/z^2\) blows up to order minus two.
On a curved surface we have to make sure this order is independent
of which microscope (which chart) we used to look. It is, and that
single fact lets us define \emph{vanishing order} unambiguously at
every point.

The second move is to use vanishing orders for accounting. A
\emph{divisor} is just a tally sheet: ``vanishes to order three
here, blows up to order two there, otherwise zero.'' Divisors form
an abelian group under addition. The set of zeros and poles of a
nonzero meromorphic function is a finite, signed tally --- a
\emph{principal divisor} --- and the principle of conservation we'll
prove (``a meromorphic function has equally many zeros and poles,
counted with multiplicity'') becomes the slogan that the degree of a
principal divisor is zero. From here, the deeper theorems
(Riemann--Roch, the genus--zero classification, Abel's theorem) are
each refinements of this very simple bookkeeping.

Why bother? Because the bookkeeping is what later turns into the
\emph{Picard group}, the \emph{Jacobian}, and the bridge between
algebra and geometry on which the rest of the document rests. A
clean treatment of vanishing orders and divisors here lets every
later argument feel like algebra, even when it's secretly analysis.
\end{layman}

Throughout, \(X,Y,Z\) denote compact connected Riemann surfaces, and maps
between them are holomorphic unless otherwise specified. Compactness implies
that every holomorphic function \(X\to\C\) is constant. Holomorphic maps
between compact Riemann surfaces are either constant or finite branched
coverings.

\subsection{Order of vanishing}

Throughout, all charts are holomorphic. We work locally and then glue.

\begin{definition}[Order of vanishing of a meromorphic germ at a point]
\label{def:vanishing-order}
For a holomorphic chart \(\varphi:U\to\C\) sending \(p\mapsto 0\) and a
meromorphic germ \(f\) at \(p\), the order of vanishing
\(\ord_p(f)\in\Z\cup\{+\infty\}\) is the order of the Laurent series of
\(f\circ\varphi^{-1}\) at \(0\). The convention is
\(\ord_p(0)=+\infty\) and \(\ord_p(f)<0\) for poles. The value is
independent of the chart.
\depends{Mathlib's \texttt{analyticOrderAt} for normed spaces; chart
independence proved via composition of analytic equivalences.}
\lean{JacobianChallenge.HolomorphicForms.VanishingOrder.MeromorphicAtX, JacobianChallenge.HolomorphicForms.VanishingOrder.orderAt, JacobianChallenge.HolomorphicForms.VanishingOrder.orderAt_eq_meromorphicOrderAt_of_mem_maximalAtlas}
\leanok
\end{definition}

\begin{layman}
Near any single point on the surface, a function does one of three things: it
sits at a finite, nonzero value (boring), it dwindles to zero, or it blows up
to infinity. The ``order of vanishing'' is one whole number that captures how
aggressively. Order \(+1\) means the function shrinks roughly as fast as the
distance to the point; order \(+2\) means as fast as the distance squared
(twice as fast); order \(-1\) means it blows up roughly like one-over-distance.
A boring nonzero value gets order \(0\). The all-zero function gets order
\(+\infty\) by convention. The catch is that ``distance to a point'' isn't
intrinsic to a curvy surface --- you have to pick a flat coordinate chart, like
laying graph paper over a patch of globe. The lemma quietly proves that the
answer doesn't depend on which chart you pick. Why bother? This single integer
is the atom out of which divisors, principal divisors, and the whole
zero-and-pole bookkeeping of the next sections will be built.
\end{layman}

\begin{proofsketch}[Lean formalization strategy]
Mathlib v4.28 provides \texttt{MeromorphicAt} and \texttt{meromorphicOrderAt}
in \texttt{Mathlib.Analysis.Meromorphic.\{Basic, Order\}} for functions
\(f : \mathbb{k} \to E\) on a normed field, so the manifold case requires a
project-side wrapper that reduces to the chart-local statement. Concrete
plan (vetted against v4.28 by an LLM cross-check round):

\begin{enumerate}
\item Define \texttt{MeromorphicAtX (f : X $\to$ \(\C\)) (p : X)} as
  \texttt{MeromorphicAt (f $\circ$ (extChartAt $\mathcal I(\C)$ p).symm)
  (extChartAt $\mathcal I(\C)$ p p)}, using the extended chart of
  \texttt{IsManifold $\mathcal I(\C)$ $\omega$ X}.
\item Define \texttt{orderAt p f hf := meromorphicOrderAt (f $\circ$
  (extChartAt $\mathcal I(\C)$ p).symm) (extChartAt $\mathcal I(\C)$ p p) :
  WithTop $\Z$}, with \texttt{hf : MeromorphicAtX f p}.
\item Chart-independence: for two extended charts
  \(e_1, e_2\) at \(p\), the transition map
  \(g := e_2 \circ e_1^{-1}\) is analytic at \(e_1(p)\) and
  \(g(e_1(p)) = e_2(p)\); the manifold typeclass provides
  \texttt{ContMDiff} of order \(\omega\), which on the standard model
  \(\mathcal I(\C)\) means analytic. The complex inverse function theorem
  gives \(g'(e_1(p)) \ne 0\). Apply
  \texttt{MeromorphicAt.meromorphicOrderAt\_comp}
  (\texttt{Mathlib.Analysis.Meromorphic.Order} line 725) to conclude
  \(\ord_{e_1}(f \circ e_1^{-1}) = \ord_{e_2}(f \circ e_2^{-1})\).
\end{enumerate}

Estimated cost: ~250--350 LOC across one new file
(\texttt{Jacobian/HolomorphicForms/VanishingOrder.lean}). The transition
derivative-non-zero step is the only piece without an off-the-shelf
Mathlib lemma; it costs ~30--50 LOC and reduces to the complex inverse
function theorem (\texttt{Mathlib.Analysis.Calculus.InverseFunctionTheorem}).
Naming note: \texttt{PartialHomeomorph}, not \texttt{LocalHomeomorph}
(already renamed in pre-v4.28).
\end{proofsketch}

\begin{lemma}[Discreteness of the divisor support]
\label{lem:divisor-discrete}
\uses{def:vanishing-order}
For a nonzero meromorphic function \(f\) on \(X\), the set
\(\{p\in X:\ord_p(f)\ne 0\}\) has no accumulation point.
\lean{JacobianChallenge.Blueprint.divisor_discrete}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{layman}
Take a meromorphic function --- one that's allowed finitely many points where
it hits zero or blows up. The claim is that those special points can never
crowd together: between any two of them there's always some breathing room.
Said another way, you can't have an infinite sequence of zeros or poles
clustering around a single spot. This is the same magic that lets a
polynomial have only finitely many roots in any bounded region: complex
analytic functions are rigid, and ``rigid'' rules out a sea of nearby
misbehavior. Why bother? Together with compactness of the surface (the next
step), this turns ``the set of interesting points'' from something
potentially wild into a tidy finite list --- exactly the input the divisor
bookkeeping needs.
\end{layman}

\begin{proofsketch}
Locally, in a chart \(\varphi\), \(f\circ\varphi^{-1}\) is meromorphic on
an open subset of \(\C\). Either the Laurent series at \(\varphi(p)\)
vanishes identically (impossible for a nonzero meromorphic function on
a connected open set, by the identity theorem), or it has finite order.
Finite order at a point \(p\) gives a chart neighborhood on which \(f\)
has no zeros and no poles other than at \(p\). The identity theorem
applied across the chart atlas globalizes this.
\end{proofsketch}

\begin{lemma}[Compactness gives finite divisor support]
\label{lem:divisor-finite-support}
\uses{lem:divisor-discrete}
For a nonzero meromorphic function \(f\) on the compact Riemann surface
\(X\), the set \(\{p\in X:\ord_p(f)\ne 0\}\) is finite.
\lean{JacobianChallenge.Blueprint.divisor_finite_support}
\leanok
\end{lemma}

\begin{layman}
Combine two facts and you get a clean conclusion. Fact one: the surface is
compact, meaning it's closed and bounded --- a sphere, a donut, a pretzel,
never an infinitely-extending plane. Fact two (just shown): the points where
a meromorphic function vanishes or blows up never crowd together. On a
compact space, any infinite set of points has to crowd somewhere --- there's
nowhere for them to spread out to. So if our points refuse to crowd, there
can only be finitely many of them. Why bother? This is the moment the
abstract ``divisor'' machinery snaps into focus: each meromorphic function
gives a finite shopping list of zeros and poles, with concrete
weights, ready to be added and compared.
\end{layman}

\begin{proof}\leanok
A subset of a compact space with no accumulation point is finite.
\end{proof}

\subsection{Divisor group}

\begin{definition}[Divisor group]
\label{def:divisor}
The divisor group \(\Div(X)\) is the free abelian group on the points of
\(X\). A divisor is a formal finite \(\Z\)-linear combination
\(D=\sum_{p}n_p\,p\) with \(n_p\in\Z\) and \(\{p:n_p\ne 0\}\) finite.
\depends{Mathlib's \texttt{FreeAbelianGroup}.}
\lean{JacobianChallenge.Blueprint.Divisor}
\leanok
\end{definition}

\begin{layman}
A divisor is just a bookkeeping device: pick finitely many points on the
surface, attach a whole-number weight to each (positive, negative, or
zero), and that whole tagged collection is your ``divisor.'' Think of it
as a shopping list with quantities --- except some items can have a
negative count, meaning ``minus three of those.'' Two divisors get
``added'' the obvious way: at each shared point, sum the weights; at
points that appear in only one of them, just carry the weight over.
This makes divisors form a group, in the same way that whole numbers do
under ordinary addition. Why bother? Because later we'll use divisors to
keep score: where does a function vanish, where does it blow up, by how
much. The bookkeeping turns out to be exactly what's needed to ask
``how many independent functions can have these zeros and these poles?''
--- which is the central question of Riemann--Roch.
\end{layman}

\begin{definition}[Degree of a divisor]
\label{def:divisor-degree}
\uses{def:divisor}
The degree map \(\deg:\Div(X)\to\Z\) sends \(D=\sum_p n_p\,p\) to
\(\sum_p n_p\). It is a group homomorphism.
\lean{JacobianChallenge.Blueprint.Divisor.degree}
\leanok
\end{definition}

\begin{layman}
We saw that a divisor is a tagged collection of points with whole-number
weights --- a shopping list, possibly with negative quantities. The
\emph{degree} is the simplest thing you can do with such a list: just add up
all the weights, ignoring which points they were attached to. Three apples,
minus two oranges, plus seven pears? Degree \(3 - 2 + 7 = 8\). It's the
checkout total without caring what's in the cart. This map respects addition:
combining two shopping lists and totalling is the same as totalling each list
and then adding the totals. So degree is a clean homomorphism from divisors
to the integers. Why bother? It splits divisors into ``net positive,''
``net negative,'' and ``net zero'' classes. The degree-zero divisors are the
ones that can come from a single meromorphic function, and they're the input
to the Abel--Jacobi map down the road.
\end{layman}

\begin{proofsketch}[Lean formalization strategy]
Mathlib v4.28 already has \texttt{FreeAbelianGroup} in
\texttt{Mathlib.GroupTheory.FreeAbelianGroup}, with the universal map
\texttt{FreeAbelianGroup.lift : ($\alpha\to\beta$) $\simeq$
(FreeAbelianGroup $\alpha\to_+\beta$)} and the simp lemma
\texttt{FreeAbelianGroup.lift\_apply\_of}. Cross-checked against v4.28 by
an LLM round (ChatGPT proposed the wrapper, Grok confirmed name
correctness against the v4.28 source and refined the instance pattern).
The two definitions reduce to a $\sim$15--25 LOC file
\texttt{Jacobian/HolomorphicForms/Divisor.lean}:
\begin{enumerate}
\item \texttt{def Divisor (X : Type u) : Type u := FreeAbelianGroup X},
  with \texttt{instance : AddCommGroup (Divisor X) := inferInstanceAs \_}.
  No \texttt{noncomputable}, no \texttt{@[reducible]}, no extra type
  classes on \(X\) (the blueprint says ``free abelian group on the
  points of \(X\)'' --- \(X\) is a plain \texttt{Type}).
\item \texttt{def Divisor.of (p : X) : Divisor X := FreeAbelianGroup.of p}.
\item \texttt{def Divisor.degree : Divisor X $\to_+$ $\Z$ :=
  FreeAbelianGroup.lift (fun \_ => 1)}.
\item \texttt{@[simp] theorem degree\_of (p : X) :
  degree (of p) = 1 := by simp [degree, of]} ---
  one-line proof via \texttt{FreeAbelianGroup.lift\_apply\_of}.
\end{enumerate}
No new sorries, no Mathlib gap. This is a clean leaf chosen specifically
to verify the cloud SessionStart cache-prime hook.
\end{proofsketch}

\subsection{Meromorphic functions, principal divisors, principal degree}

\begin{definition}[Meromorphic functions on a compact Riemann surface]
\label{def:meromorphic-function}
\uses{def:vanishing-order}
The set \(\Mer(X)\) of meromorphic functions on \(X\) is the set of
sections of the sheaf of meromorphic germs. \(\Mer(X)\) is a field with
the constants \(\C\) embedded as constant functions, and a nonzero
\(f\in\Mer(X)\) defines a holomorphic map \(X\to\CPone\) with poles at
\(\{p:\ord_p(f)<0\}\).
\depends{Mathlib has \texttt{MeromorphicAt} on normed spaces; gluing along a
chart atlas to a global field on \(X\) is project-side work.}
\lean{JacobianChallenge.HolomorphicForms.MeromorphicFunctionType}
\leanok
\end{definition}

\begin{layman}
A holomorphic function on the surface is one that's complex-differentiable
everywhere --- the smoothest, most rigid kind there is. A \emph{meromorphic}
function relaxes this slightly: it's holomorphic except at finitely many
points where it's allowed to blow up to infinity in a controlled way (think
\(1/z\) at the origin). On a compact surface, the holomorphic functions are
boring --- they have to be constants --- but the meromorphic ones form a rich
field, the kind of algebraic object where you can add, subtract, multiply,
and divide, just like rational numbers. You can also picture a meromorphic
function as a holomorphic map to the Riemann sphere --- the complex plane with
a single extra ``point at infinity'' --- where ``blowing up'' just means
``going to that point.'' Why bother? Meromorphic functions are the test
functions of the entire theory: their zeros and poles generate principal
divisors, and Riemann--Roch is the question of how many of them fit a given
pattern.
\end{layman}

\begin{definition}[Principal divisor of a meromorphic function]
\label{def:principal-divisor}
\uses{def:divisor,def:meromorphic-function,lem:divisor-finite-support}
For a nonzero \(f\in\Mer(X)\),
\[
  (f) := \sum_{p\in X} \ord_p(f)\,p \in \Div(X).
\]
The map \((\,\cdot\,):\Mer(X)^{\times}\to\Div(X)\) is a group
homomorphism (\(\Mer(X)^{\times}\) under multiplication).
\lean{JacobianChallenge.Blueprint.principalDivisor}
\leanok
\end{definition}

\begin{layman}
Each nonzero meromorphic function comes with a free shopping list: tag every
zero with a positive weight equal to its order (a double zero gets a 2), tag
every pole with a negative weight equal to how badly it blows up (a simple
pole gets a \(-1\)), and ignore every other point. The result is the
\emph{principal divisor} of the function. Multiplying two functions adds
their shopping lists --- zeros stack, poles stack, and a zero meeting a
matching pole cancels --- so this is a group homomorphism from the
multiplicative group of nonzero meromorphic functions into the additive
group of divisors. Why bother? Principal divisors are the
``trivially achievable'' divisors. The big question of the whole theory is:
which other divisors are reachable, in what sense, and what's the
obstruction? The Jacobian variety, several sections later, is in spirit
exactly the answer to that obstruction question.
\end{layman}

\begin{definition}[Principal divisors]
\label{def:principal-divisors}
\uses{def:principal-divisor}
The subgroup of principal divisors is
\(\Prin(X) := \{(f) : f\in\Mer(X)^{\times}\}\subset\Div(X)\).
\lean{JacobianChallenge.Blueprint.principalDivisors}
\leanok
\end{definition}

\begin{layman}
Collect every shopping list that comes from a meromorphic function in the
way just described. This collection is closed under addition (the product
of two functions gives the sum of their lists), closed under negation (one
over the function flips signs), and contains the empty list (the constant
function \(1\)). So the principal divisors form a subgroup inside the group
of all divisors. Picture all divisors as a vast warehouse of imaginable
shopping lists, and the principal divisors as the narrow aisle of lists
that actually correspond to a real meromorphic function. Why bother?
The quotient of all divisors by this subgroup is the
\emph{divisor class group} (and, in degree zero, the Picard group). That
quotient is exactly what the Jacobian variety geometrizes: we're
quotienting out the ``trivial'' equivalence so we can study what's left.
\end{layman}

\begin{theorem}[Principal divisors have degree zero]
\label{thm:principal-degree-zero}
\uses{def:principal-divisor,def:divisor-degree}
For every nonzero \(f\in\Mer(X)\), \(\deg(f)=0\).
\lean{JacobianChallenge.Blueprint.principal_degree_zero}
\leanok
\end{theorem}
\begin{proof}\leanok\end{proof}

\begin{layman}
Take any nonzero meromorphic function and write down its shopping list of
zeros and poles, weighted by order. The claim: the weights always sum to
exactly zero. Zeros and poles are perfectly balanced --- for every total of
\(k\) units of vanishing, there's an equal total of pole strength elsewhere.
A physical picture: think of the function as defining a flow on the surface;
zeros are ``sources,'' poles are ``sinks,'' and on a closed surface with
no boundary, sources and sinks must balance globally --- there's nowhere
else for the flow to go. Why bother? It tells us that every principal
divisor lives entirely inside the degree-zero divisors. So when we later
quotient out, we'll be quotienting inside one fixed degree level --- exactly
the structural setup the Jacobian needs.
\end{layman}

\begin{proofsketch}
The classical proof uses the argument principle on a polygonal model of
\(X\): the integral
\(\frac{1}{2\pi i}\oint_{\partial X}\,d\!\log f\) counts zeros minus
poles, but the polygon's boundary cancels out by the identification of
opposite sides, so the difference is zero. Equivalently, this is a
special case of \(\sum\Res = 0\) for the meromorphic 1-form \(df/f\).
\end{proofsketch}

\subsection{Meromorphic functions as maps to \texorpdfstring{\(\CPone\)}{CP1}}

\begin{definition}[Map to \(\CPone\) associated to a meromorphic function]
\label{def:meromorphic-to-cp1}
\uses{def:meromorphic-function}
For nonzero \(f\in\Mer(X)\), define \(\widehat{f}:X\to\CPone\) by
\(\widehat{f}(p)=f(p)\) where \(f\) is holomorphic at \(p\) and
\(\widehat{f}(p)=\infty\) at poles. This is a holomorphic map of compact
Riemann surfaces.
\lean{JacobianChallenge.HolomorphicForms.meromorphicToCp1}
\leanok
\end{definition}

\begin{layman}
Any meromorphic function naturally extends to a map into the \emph{Riemann
sphere} --- the complex plane plus a single extra ``point at infinity''
wrapped around like the north pole of a globe. Wherever the function gives
a finite value, send the point there as usual; wherever the function blows
up, send the point to that distinguished north pole. Suddenly there's
nothing to apologize for: poles are just the preimage of one specific
extra point, no different from any other value. The blown-up
discontinuity becomes a smooth, well-defined output. And this extended
map is holomorphic everywhere. Why bother? It converts ``meromorphic
function with ugly poles'' into ``holomorphic map between two compact
surfaces,'' which unlocks topological tools like degree, ramification,
and covering theory --- exactly what we'll need to analyze maps between
Riemann surfaces.
\end{layman}

\begin{theorem}[Meromorphic-to-\(\CPone\) bijection]
\label{thm:meromorphic-as-cp1-map}
\uses{def:meromorphic-to-cp1}
The map \(f\mapsto\widehat{f}\) is a bijection between nonzero
meromorphic functions on \(X\) and nonconstant holomorphic maps
\(X\to\CPone\).
\lean{JacobianChallenge.Blueprint.meromorphic_as_cp1_map}
\leanok
\end{theorem}
\begin{proof}\leanok\end{proof}

\begin{layman}
The promotion to a sphere-valued map isn't just a convenience --- it's a
perfect two-way correspondence. Every nonzero meromorphic function gives a
nonconstant holomorphic map to the Riemann sphere; every nonconstant
holomorphic map to the Riemann sphere comes from a unique meromorphic
function (just read off its values, with the preimages of the north pole
becoming poles). The two points of view are completely interchangeable:
``meromorphic function'' and ``map to the sphere'' are the same object
wearing different clothes. Why bother? It lets us swap fluently between
the algebraic picture (functions you can multiply and divide) and the
geometric picture (maps with fibers, branch points, and degree). Most of
the cleverness in classical Riemann surface theory lives in choosing the
right outfit for the moment.
\end{layman}

\begin{proofsketch}
Forward: a meromorphic function on \(X\) is exactly a holomorphic
section of \(X\to\CPone\) defined off the polar set, with continuous
extension to \(\infty\) at the polar set; the extension is forced and
holomorphic. Reverse: given \(g:X\to\CPone\), restrict to
\(g^{-1}(\C)\) and observe the result is holomorphic, with the
preimages of \(\infty\) becoming poles.
\end{proofsketch}

\subsection{Riemann-Roch space}

\begin{definition}[Riemann-Roch space \(L(D)\)]
\label{def:riemann-roch-space}
\uses{def:divisor,def:meromorphic-function,def:principal-divisor}
For a divisor \(D\),
\[
  L(D) := \{f\in\Mer(X) : (f)+D\ge 0\}\cup\{0\}.
\]
\lean{JacobianChallenge.Blueprint.riemannRochSpace}
\leanok
\end{definition}

\begin{layman}
Pick a divisor --- your shopping list of points with whole-number weights.
The associated Riemann--Roch space is the collection of all meromorphic
functions whose own shopping list is, position by position, no worse than
the one you picked. Concretely: if your list permits a double pole at a
point, the function is allowed to blow up at most that badly there; if
your list demands a zero at another point, the function must vanish there.
(The zero function is included by convention.) Think of the divisor as a
budget --- points where poles are permitted, points where zeros are required ---
and the Riemann--Roch space as every meromorphic function that lives within
budget. Why bother? The dimension of this space, as a complex vector
space, is the central quantity of the whole classical theory. Riemann--Roch
is a formula computing exactly how many independent functions fit any
given budget, and from that flows everything about line bundles,
embeddings, and the geometry of curves.
\end{layman}

\begin{lemma}[\(L(D)\) is a complex vector space]
\label{lem:riemann-roch-space-vector}
\uses{def:riemann-roch-space}
\(L(D)\) is a \(\C\)-vector subspace of \(\Mer(X)\).
\lean{JacobianChallenge.Blueprint.riemann_roch_space_vector}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{layman}
The Riemann--Roch space --- meromorphic functions fitting a given budget of
zeros and poles --- is closed under the two basic vector-space operations.
If two functions both fit the budget, their sum still fits the budget
(the worst poles can't get worse by adding); and scaling a function by a
complex number doesn't change its zeros or poles at all. So this set
isn't just a collection, it's a complex vector space, with a finite
dimension we can count. Why bother? A vector space is the playground of
linear algebra. Once we know Riemann--Roch spaces are vector spaces, we
can ask: what's their dimension? That single number is the protagonist
of the Riemann--Roch theorem.
\end{layman}

\subsection{Aggregate input}

\begin{theorem}[Classical input: Meromorphic functions and divisors (umbrella)]
\label{input:divisors}
\uses{def:divisor,def:divisor-degree,def:meromorphic-function,def:principal-divisor,def:principal-divisors,thm:principal-degree-zero,def:meromorphic-to-cp1,thm:meromorphic-as-cp1-map,def:riemann-roch-space,lem:riemann-roch-space-vector}
\lean{JacobianChallenge.Blueprint.input_divisors_holds}
\leanok
The classical theory of meromorphic functions, divisors, principal
divisors, the degree map, and Riemann-Roch spaces on a compact
Riemann surface, packaged as a single dependency for downstream
classical inputs (Riemann-Roch, Abel's theorem).
\end{theorem}
\begin{proof}\leanok\end{proof}

\begin{layman}
We package every classical fact above into one named bundle: the theory
of meromorphic functions, divisors, principal divisors, the degree map,
and Riemann--Roch spaces on a compact Riemann surface. Each piece is more
than a century old, fully understood by professionals, and, frankly,
hundreds of pages to formalize from first principles in a proof
assistant. Rather than reinvent that wheel inside this project, we cite
the whole package as a single classical input and build the rest of the
proof on top of it. Why bother? Modular accounting. Future steps depend
on \emph{the package}, so any later upgrade that swaps the package for
a fully-formalized version will slot right in without disturbing the
proof of the main theorem.
\end{layman}

\begin{formalizationnote}
The repository currently has substantial chart and path-integration
infrastructure, but not a full divisor or meromorphic-function theory on
compact Riemann surfaces. The pieces above are individually
project-sized but each is a clean stand-alone obligation; some
(\texttt{def:divisor}, \texttt{def:divisor-degree}) reduce to existing
Mathlib infrastructure (\texttt{FreeAbelianGroup}). Others
(\texttt{def:meromorphic-function}, \texttt{thm:principal-degree-zero})
require sheaf-of-meromorphic-germs gluing or argument-principle work
that is not yet in Mathlib.
\end{formalizationnote}
\subsection{Stepwise refinement of \texttt{MeromorphicDegree.lean}
(sum-of-orders)}
\label{subsec:meromorphic-degree-refinement}
\uses{lem:meromorphic-local-normalization,lem:meromorphic-fiber-count-conservation}

\begin{lemma}[Local normalization of meromorphic maps]
\label{lem:meromorphic-local-normalization}
A meromorphic map locally admits the form \(z \mapsto z^k\) or \(z \mapsto 1/z^k\).
\lean{JacobianChallenge.HolomorphicForms.liftToCp1_local_kfold_ramified}
\leanok
\end{lemma}

\begin{lemma}[Conservation of fiber count]
\label{lem:meromorphic-fiber-count-conservation}
The weighted fiber count of a meromorphic map is locally constant.
\lean{JacobianChallenge.HolomorphicForms.liftToCp1_weightedFiberSum_eventually_eq}
\leanok
\end{lemma}

\code{Jacobian/HolomorphicForms/MeromorphicDegree.lean} carries two
...
\texttt{sorry}s --- continuity of the meromorphic lift over a unique
simple pole, and bijectivity of the lift from pole-divisor degree~one ---
that classify as \emph{Aristotle-BLOCKER} pending the four \texttt{sorry}s
in \code{Jacobian/Blueprint/Sec01/MeromorphicToCp1.lean}: the
chart-local holomorphicity at a finite or pole value, the chart-local
\(k\)-fold normal form, and the local conservation of the weighted
fibre count under \(k\)-fold ramification.

The intermediate file
\code{Jacobian/HolomorphicForms/MeromorphicDegreeRefinement.lean}
gives a sorry-free twenty-pass ledger for the reduction:

\begin{itemize}
\item \emph{Passes 1--4.} Continuity decomposition: continuity off the
  pole locus, continuity at the unique pole through the \(\CPone\)
  inversion chart, continuity glue from \texttt{open-cover continuity}.
\item \emph{Passes 5--12.} Bijectivity from sum-of-orders: weighted fibre
  count over \(\infty\) equals \(\deg(\text{poles})\), local constancy of
  the weighted sum (eventually-eq pivot from
  \texttt{Sec01.liftToCp1\_weightedFiberSum\_eventually\_eq}), global
  constancy on a connected target, surjectivity from positivity,
  injectivity from the count-equals-card identity.
\item \emph{Passes 13--17.} Bridging structure between
  \texttt{MeromorphicMapToSphere} and the \S 1
  \texttt{liftToCp1\_isHolomorphic} record, plus the
  finite-fibre-from-compact-source lemma.
\item \emph{Passes 18--20.} Final assembly markers showing both
  \texttt{MeromorphicDegree} sorries reduce to four named \S 1
  obligations.
\end{itemize}

Every pass is sorry-free; the ledger pins the dependency graph at the
type level so Aristotle work on \S 1 has a stable downstream consumer.
