\section{Holomorphic Forms and Genus}
\label{sec:holomorphic-forms-and-genus}

Let \(\HX\) be the vector space of global holomorphic one-forms. Define the
analytic genus by \(g(X)=\dim_{\C}\HX\), as in
Definition~\ref{def:analytic-genus}.

\subsection{Finite-dimensionality (analytic route)}

The project's preferred route to \(\dim_{\C}\HX<\infty\) is analytic: a
sup-norm makes \(\HX\) a normed space, Montel's theorem makes the closed
unit ball compact, and Riesz's lemma forces finite dimensionality.

\begin{definition}[Fiber norm on the cotangent bundle]
\label{def:cotangent-fiber-norm}
\lean{JacobianChallenge.Blueprint.cotangentFiberNorm}
For each \(x\in X\) the cotangent fiber
\(T^{*}_{x}X = T_{x}X \to_{\C}\C\) is a one-dimensional complex vector
space. Equip it with the canonical operator norm
\(\|v\|_{x} := \sup_{\xi\in T_{x}X,\ \|\xi\|=1} |v(\xi)|\),
where \(\|\xi\|\) is taken via any chart isomorphism
\(\dd\varphi_{x}: T_{x}X \xrightarrow{\sim} \C\) (any two chart norms
on a one-dimensional fiber differ by a positive scalar, so the operator
norm on \(T^{*}_{x}X\) inherits a chart-independent equivalence class;
to fix a single function rather than an equivalence class we choose
the chart norm coming from the preferred \texttt{chartAt} of the
\texttt{ChartedSpace} structure).

The resulting function
\((x, v) \mapsto \|v\|_{x}\) is continuous on the total space of
\(T^{*}X\): on each chart neighbourhood \(U\) the trivialisation
identifies \(T^{*}_{x}X\) with \(\C\to_{\C}\C\) by an isomorphism
varying continuously in \(x\), and the operator norm is itself
continuous on \(\C\to_{\C}\C\); composition of continuous maps is
continuous. (See Mathlib
\texttt{Bundle.ContinuousLinearMap.vectorBundle} for the vector-bundle
structure on \(T^{*}X\), and the operator-norm continuity from
\texttt{ContinuousLinearMap.opNorm\_le\_iff}.)
\depends{Mathlib operator norm on \(\C\to_{\C}\C\); project-side
\texttt{CotangentSpace} from
\texttt{Jacobian/HolomorphicForms/CotangentBundle.lean}.}
\leanok
\end{definition}

\begin{layman}
At each point of the surface, a holomorphic 1-form picks out a tiny
linear gadget — a local rule that turns a direction into a complex number.
This local gadget lives in a one-dimensional space called the
\emph{cotangent fiber}, and we want to measure how big the gadget is.
The trick: borrow a coordinate chart at the point (a bit of flat graph
paper laid over the curvy surface), use it to declare a unit length on
tangent directions, and then ask, ``what's the largest absolute value the
gadget outputs on a unit-length input?'' That maximum is its norm.
Different charts give slightly different units, but we standardize by
always using the canonical chart that's already attached to the surface's
atlas. Why bother? With a length on every fiber, we can ask whether a
1-form is big or small at any point — a prerequisite to defining a global
``size'' on the whole space of holomorphic 1-forms in the next step.
\end{layman}

\begin{definition}[Sup norm on \(\HX\)]
\label{def:holomorphic-sup-norm}
\uses{def:cotangent-fiber-norm}
\lean{JacobianChallenge.Blueprint.holomorphicSupNorm}
For \(\omega\in\HX\), define
\[
  \|\omega\| := \sup_{x\in X}\|\omega_x\|_{x},
\]
where \(\|\omega_x\|_{x}\) is the fiber norm of
Definition~\ref{def:cotangent-fiber-norm}. Compactness of \(X\) plus
continuity of \(x \mapsto \|\omega_x\|_{x}\) (the composition of the
continuous section \(\omega\) with the continuous fiber-norm function)
implies the sup is attained and finite, by the extreme value theorem
(Mathlib \texttt{IsCompact.exists\_isMaxOn}). The standard checks
\(\|\omega\|=0\iff \omega=0\), \(\|\lambda\omega\|=|\lambda|\|\omega\|\)
and the triangle inequality follow pointwise from the corresponding
properties of the fiber norm; this makes \((\HX,\|\cdot\|)\) a normed
\(\C\)-vector space. (Cf.\ Forster, \emph{Lectures on Riemann
Surfaces}, \S 14.)
\leanok
\end{definition}

\begin{layman}
We've measured the size of a holomorphic 1-form at each point. To get a
single number summarizing the whole 1-form on the whole surface, just
take the largest pointwise size that ever occurs. This \emph{supremum
norm} is finite because the surface is compact, the size function is
continuous, and a continuous function on a closed-and-bounded space
always attains a maximum (no sneaking off to infinity). The standard
checks pass: the norm is zero exactly for the zero 1-form, scales
correctly under multiplication by a complex number, and obeys the
triangle inequality. So the space of holomorphic 1-forms becomes a
\emph{normed vector space} — the same structural home as Euclidean space
or any Banach space. Why bother? Once you have a norm, you have notions
of distance, convergence, balls, and compactness. The whole analytic
strategy for proving finite-dimensionality runs on those notions.
\end{layman}

\begin{lemma}[Local coefficient bound on a chart]
\label{lem:chart-coefficient-bound}
\uses{def:holomorphic-sup-norm}
\lean{JacobianChallenge.Blueprint.chart_coefficient_bound}
Let \(\varphi:U\to V\subseteq\C\) be a chart in the holomorphic atlas
of \(X\). On \(U\) every \(\omega\in\HX\) admits a unique
representation \(\omega = h_{\varphi}(z)\,dz\) with
\(h_{\varphi} : V \to \C\) holomorphic. Then there is a constant
\(C_{\varphi}\ge 0\), depending only on the chart \(\varphi\) (and the
choice of fiber norm on \(T^{*}X\)), such that
\[
  |h_{\varphi}(z)| \;\le\; C_{\varphi}\,\|\omega\|
  \qquad\text{for all } z \in V.
\]
\leanok
\end{lemma}

\begin{layman}
Open up a single coordinate chart — a flat patch of graph paper laid over
a piece of the surface. On that patch, every holomorphic 1-form looks
like an ordinary holomorphic function multiplied by the differential of
the coordinate. The lemma says the size of that ordinary function at
each point is bounded above by a fixed constant — depending only on the
chart — times the global supremum norm of the 1-form. In plain terms,
shrinking a 1-form globally shrinks its local coefficient on the chart
by at most a fixed factor; the chart can't blow up the constants behind
your back. Why bother? It's the bridge between the abstract norm on the
space of 1-forms and the concrete behavior of holomorphic functions on
disks in the plane, where Mathlib's existing complex-analysis toolbox
already applies. We need that bridge to invoke Cauchy's estimates and
Montel's theorem in the next step.
\end{layman}

\begin{proofsketch}
Set \(p := \varphi^{-1}(z)\). The chart trivialisation identifies the
fiber \(T^{*}_{p}X\) with \(\C \to_{\C} \C\) isometrically up to a
chart-dependent positive constant \(C_{\varphi}^{-1}\); under this
identification \(\omega_{p}\) corresponds to the linear map
\(\xi\mapsto h_{\varphi}(z)\,\xi\), whose operator norm is exactly
\(|h_{\varphi}(z)|\). Therefore
\(|h_{\varphi}(z)| \le C_{\varphi}\,\|\omega_{p}\|_{p} \le
C_{\varphi}\,\|\omega\|\). The constant \(C_{\varphi}\) is bounded by
the supremum on the (relatively compact) chart image of the
trivialisation comparison factor, which is finite by continuity.
\end{proofsketch}

\begin{lemma}[Montel compactness]
\label{lem:montel-compactness}
\uses{def:holomorphic-sup-norm,lem:chart-coefficient-bound}
\lean{JacobianChallenge.Blueprint.montel_compactness}
The closed unit ball of \(\HX\) is sequentially compact: every sequence
\(\omega_n\in\HX\) with \(\|\omega_n\|\le 1\) for all \(n\) admits a
strictly increasing \(\varphi:\N\to\N\) and a limit
\(\omega_\infty\in\HX\) with \(\|\omega_\infty\|\le 1\) such that
\(\|\omega_{\varphi(n)} - \omega_\infty\| \to 0\) as \(n\to\infty\)
(equivalently, \(\omega_{\varphi(n)} \to \omega_\infty\) uniformly on
\(X\)).
\leanok
\end{lemma}

\begin{layman}
Now the analytic punchline. Take any sequence of holomorphic 1-forms
whose norms are all bounded by 1 — the closed unit ball. The claim: you
can always extract a subsequence converging uniformly on the whole
surface to another holomorphic 1-form of norm at most 1. This is Montel's
theorem in disguise — magic special to holomorphic functions, with no
analogue for plain continuous or merely smooth functions. The proof works
chart by chart: in each chart, Cauchy's integral formula bounds
derivatives, which forces the sequence to be \emph{equicontinuous} — every
form in the sequence wiggles at the same controlled rate. Arzelà–Ascoli
then extracts a convergent subsequence, and the chartwise limits glue
into a global holomorphic limit by Weierstrass's convergence theorem
(uniform limits of holomorphic functions are again holomorphic). Why
bother? It says the unit ball is sequentially compact — a heavy hammer
that, in normed spaces, is the trademark signature of being
finite-dimensional.
\end{layman}

\begin{proofsketch}
\emph{Step 1: finite chart cover.} Compactness of \(X\) supplies a
finite atlas \(\{(U_i,\varphi_i)\}_{i=1}^{N}\) with each
\(\varphi_i(U_i) \supseteq \overline{B(c_i, R_i)}\); choose
\(0 < r_i < R_i\) with \(\bigcup_i \varphi_i^{-1}(B(c_i, r_i)) = X\).

\emph{Step 2: chartwise sup bound.} Lemma~\ref{lem:chart-coefficient-bound}
gives constants \(C_i\) such that the chart coefficient
\(h_{n,i}\) of \(\omega_n\) on \(U_i\) satisfies
\(|h_{n,i}(z)| \le C_i\) for all \(z \in \overline{B(c_i, R_i)}\) and
all \(n\).

\emph{Step 3: Cauchy estimates yield equicontinuity.} For
\(z \in \overline{B(c_i, r_i)}\) the Cauchy integral formula for the
derivative,
\(h_{n,i}'(z) = \frac{1}{2\pi i}\oint_{|w-c_i|=R_i}
\frac{h_{n,i}(w)}{(w-z)^2}\,dw\),
combined with \(|w-z| \ge R_i - r_i\), gives
\(|h_{n,i}'(z)| \le C_i \,R_i / (R_i - r_i)^2\). The family
\(\{h_{n,i}\}\) is therefore uniformly Lipschitz, hence equicontinuous,
on \(\overline{B(c_i, r_i)}\). (Mathlib:
\texttt{DiffContOnCl.circleIntegral\_sub\_inv\_smul} for the
Cauchy formula;
\texttt{circleIntegral.norm\_integral\_le\_of\_norm\_le\_const} for the
\(L^{\infty}\)–to–integral bound.)

\emph{Step 4: Arzelà–Ascoli on each chart.} The Arzelà–Ascoli theorem
(Mathlib \texttt{ArzelaAscoli.isCompact\_closure\_of\_isClosedEmbedding})
extracts a subsequence converging uniformly on
\(\overline{B(c_i, r_i)}\). Iterating across the \(N\) charts
diagonally produces a single subsequence
\(\omega_{\varphi(n)}\) whose chart restrictions all converge
uniformly.

\emph{Step 5: glue and pass to the limit.} The chartwise uniform
limits agree on overlaps (because they are obtained from a single
diagonal subsequence), so they assemble into a function on \(X\) which
is the uniform limit of \(\omega_{\varphi(n)}\). By Weierstrass's
convergence theorem (uniform limit of holomorphic functions is
holomorphic; cf.\ Forster \S 14 or Griffiths–Harris pp.~7–8) the chart
coefficients of the limit are again holomorphic, so the limit is a
holomorphic 1-form \(\omega_\infty\). The sup-norm bound
\(\|\omega_\infty\|\le 1\) follows by taking the limit in
\(|h_{\varphi(n),i}(z)|\le 1\) (with our normalisation; if not unit
norm, by passing to the limit in the explicit estimate).
\end{proofsketch}

\begin{theorem}[Closed unit ball is compact]
\label{thm:hone-unit-ball-compact}
\uses{lem:montel-compactness}
\lean{JacobianChallenge.Blueprint.hone_unit_ball_compact}
Under any normed-\(\C\)-vector-space realisation of \(\HX\) whose norm
agrees with the sup norm of
Definition~\ref{def:holomorphic-sup-norm}, the closed unit ball
\(\overline{B}(0,1) = \{\omega \in \HX : \|\omega\|\le 1\}\) is
(topologically) compact.
\leanok
\end{theorem}

\begin{layman}
The previous lemma extracted convergent subsequences — that's
\emph{sequential} compactness. This theorem upgrades it to ordinary
\emph{topological} compactness, the textbook ``every open cover has a
finite subcover'' kind. The two flavors agree in any normed space,
because such spaces are metrisable, and in metric spaces sequential and
topological compactness are the same notion. So the closed unit ball of
holomorphic 1-forms — the set of forms with norm at most 1 — is compact in
the textbook sense. Why bother? Compactness of a closed ball is one of
those innocent-sounding facts that's actually a structural giveaway: in
a normed space, it \emph{forces} the space to be finite-dimensional.
That's the next step.
\end{layman}

\begin{proofsketch}
A normed space is metrisable, hence first-countable; in a first-countable
space sequential compactness and topological compactness coincide
(Mathlib \texttt{UniformSpace.isCompact\_iff\_isSeqCompact} or
\texttt{IsSeqCompact.isCompact}). Apply
Lemma~\ref{lem:montel-compactness} to obtain sequential compactness of
the closed unit ball, then convert. The closed unit ball is closed in
the metric topology by continuity of the norm, so the conclusion is
exactly \texttt{IsCompact (Metric.closedBall 0 1)}.
\end{proofsketch}

\begin{theorem}[Finite-dimensionality from Riesz]
\label{thm:fd-from-riesz}
\uses{thm:hone-unit-ball-compact}
\lean{JacobianChallenge.Blueprint.fd_from_riesz}
A normed \(\C\)-vector space whose closed ball of some positive radius
is compact is finite-dimensional. This is Riesz's lemma; in Mathlib it
is \texttt{FiniteDimensional.of\_isCompact\_closedBall} (file
\texttt{Mathlib/Analysis/Normed/Module/FiniteDimension.lean}). Applied
to a normed-space realisation of \(\HX\) supplied by
Theorem~\ref{thm:hone-unit-ball-compact}, this gives
\(\dim_{\C}\HX<\infty\).
\depends{Mathlib's
\texttt{FiniteDimensional.of\_isCompact\_closedBall}.}
\leanok
\end{theorem}

\begin{layman}
Here's a surprising fact called Riesz's lemma: in any normed vector
space, if even a single closed ball of positive radius is compact, then
the whole space must be finite-dimensional. The intuition is that
infinite-dimensional spaces are too roomy to be compact — you can always
find a sequence of unit-distance-apart points that never converges, and
compactness rules this out, so room runs out. Mathlib already has this
packaged. Apply it to our setting: the closed unit ball of holomorphic
1-forms is compact (just shown), therefore the space of holomorphic
1-forms is finite-dimensional. Why bother? This is the headline
conclusion of the entire chapter. The genus of the surface — defined as
the dimension of this space — is now guaranteed to be a finite whole
number. Without it, the whole rest of the project (lattices, Jacobians,
Abel–Jacobi maps) would have nothing to grab onto.
\end{layman}

\begin{proofsketch}
Direct invocation of
\texttt{FiniteDimensional.of\_isCompact\_closedBall} \(\C\) \texttt{one\_pos\;h}
where \(h\) is the conclusion of
Theorem~\ref{thm:hone-unit-ball-compact} for the chosen realisation.
\end{proofsketch}

\begin{theorem}[Classical input: Finite-dimensionality (umbrella)]
\label{input:finite-dimensionality}
\uses{thm:fd-from-riesz}
\lean{JacobianChallenge.Blueprint.input_finite_dimensionality}
\leanok
For any normed-\(\C\)-vector-space realisation \(H\) of \(\HX\) whose
norm equals the sup norm, \(H\) is finite-dimensional.

This is the umbrella combining the analytic ingredients
(Definitions~\ref{def:cotangent-fiber-norm}--\ref{def:holomorphic-sup-norm},
Lemmas~\ref{lem:chart-coefficient-bound}--\ref{lem:montel-compactness},
Theorems~\ref{thm:hone-unit-ball-compact}--\ref{thm:fd-from-riesz}).
The alternative Riemann-Roch route (\ref{input:riemann-roch}) is named
separately and not used by the analytic finite-dim proof.
\depends{compactness, local coefficient extraction for one-forms,
Montel + Riesz.}
\end{theorem}

\begin{layman}
We package the analytic route as a single named input: any normed-space
realization of the global holomorphic 1-forms whose norm matches our
sup norm is automatically finite-dimensional. This bundles the fiber
norm, the sup norm, the local coefficient bound, Montel's compactness
theorem, the upgrade from sequential to topological compactness, and
Riesz's lemma. There's a separate route to the same conclusion via
Riemann–Roch — listed alongside as its own umbrella — but the analytic
route is the project's preferred path because its prerequisites are
mostly already in Mathlib. Why bother? Naming the umbrella keeps the
dependency graph clean. Downstream theorems depend on
``finite-dimensionality, by some route,'' rather than on the specific
analytic chain, so a future swap of routes won't disturb anything that
depends on it.
\end{layman}

\begin{proofsketch}
Combine Theorem~\ref{thm:hone-unit-ball-compact}, which gives
\texttt{IsCompact (Metric.closedBall 0 1)} on the realisation \(H\),
with Theorem~\ref{thm:fd-from-riesz}.
\end{proofsketch}

\begin{theorem}[Finite-dimensionality of holomorphic one-forms]
\label{thm:fd-holomorphic-one-forms}
\uses{input:finite-dimensionality}
\lean{JacobianChallenge.Blueprint.fd_holomorphic_one_forms}
The vector space \(\HX\) is finite-dimensional:
\(\dim_{\C}\HX<\infty\). Equivalently, the analytic genus
\(g(X)=\dim_{\C}\HX\) is a finite natural number.
\leanok
\end{theorem}

\begin{layman}
This is the headline statement, in its public form: the space of global
holomorphic 1-forms on a compact Riemann surface is finite-dimensional.
Equivalently, the analytic genus — defined as the complex dimension of
that space — is a finite natural number. We get it by taking any
project-side normed-space realization of this space, applying the
finite-dimensionality umbrella, and transporting the conclusion back.
Why bother? Genus is the single most important invariant of a Riemann
surface. ``Sphere'' has genus 0, ``donut'' has genus 1, ``two-handled
pretzel'' has genus 2, and so on up. Knowing genus is finite means we
can actually compute with it — and the finite-dimensionality of the
1-forms is what makes period lattices, Jacobians, and the entire
downstream story even formulable.
\end{layman}

\begin{proofsketch}
Transport \(\HX\) into the canonical sup-norm realisation supplied by
the project-side \texttt{HolomorphicOneFormBanachData}
(Jacobian/HolomorphicForms/CompactRiemannSurface.lean), apply
Theorem~\ref{input:finite-dimensionality} to conclude
finite-dimensionality of the realisation, and transport back along
the realisation isomorphism. (\(\C\)-linear bijections preserve
finite-dimensionality.)
\end{proofsketch}

\subsection{Riemann-Roch}

We package Riemann-Roch as a single classical input, with named
prerequisite sheaf/cohomology infrastructure that makes the
decomposition visible in the dep graph.

\begin{definition}[Sheaf cohomology of line bundles on \(X\) (placeholder)]
\label{def:sheaf-cohomology-rs}
For an invertible sheaf \(\mathcal{L}\) on \(X\) (equivalently a divisor
class), there are cohomology groups \(H^{0}(X,\mathcal{L})\) and
\(H^{1}(X,\mathcal{L})\), with \(H^{0}(X,\mathcal{O}_X(D))=L(D)\).
\depends{Sheaves on Riemann surfaces, sheaf cohomology, line bundles —
none packaged in Mathlib for compact RS at v4.28.0.}
\notready
\end{definition}

\begin{layman}
A \emph{line bundle} on the surface is a way of attaching a tiny
one-dimensional complex line to every point, varying smoothly from point
to point — like a ribbon glued onto the surface. Sometimes those ribbons
can be twisted together globally; sometimes not. The two cohomology
groups \(H^0\) and \(H^1\) are linear-algebraic gadgets that count,
respectively, how many \emph{global sections} the bundle has (smooth
choices of one point on each ribbon) and how badly the bundle is twisted
(the obstruction to having sections). For a bundle coming from a
divisor — a budget of zeros and poles — the global sections are exactly
the Riemann–Roch space we already met. The first group is harder to
picture, but the next step (Serre duality) will rewrite it as global
sections of a different bundle, making it computable. Why bother?
Riemann–Roch in its modern form is a relationship between these two
groups, and stating it cleanly requires giving them names.
\end{layman}

\begin{theorem}[Serre duality on a compact Riemann surface]
\label{thm:serre-duality-rs}
\uses{def:sheaf-cohomology-rs}
For an invertible sheaf \(\mathcal{L}\) and the canonical sheaf \(K\),
\[
  H^{1}(X,\mathcal{L})\cong H^{0}(X,K\otimes\mathcal{L}^{-1})^{\vee}.
\]
\notready
\end{theorem}

\begin{layman}
Serre duality is a magical identity. The first cohomology group of a
line bundle — the slippery, hard-to-picture one — turns out to be the
linear dual of a much friendlier object: the global sections of the
\emph{canonical} bundle twisted by the inverse of your bundle. ``Linear
dual'' just means ``space of linear functions on,'' so the dimension
matches. In short, every difficult \(H^1\) on a compact Riemann surface
quietly is a familiar \(H^0\) of something else. The canonical bundle
itself is the bundle of holomorphic 1-forms, the same finite-dimensional
space we just learned to bound. Why bother? It converts the
two-cohomology-group statement of Riemann–Roch into a single inequality
between countable, vector-space dimensions — exactly the form most useful
for producing meromorphic functions with prescribed zeros and poles.
\end{layman}

\begin{theorem}[Euler characteristic of an invertible sheaf]
\label{thm:euler-char-line-bundle}
\uses{def:sheaf-cohomology-rs,def:divisor-degree}
For an invertible sheaf \(\mathcal{L}=\mathcal{O}_X(D)\),
\(\chi(\mathcal{L}) := h^{0}(\mathcal{L}) - h^{1}(\mathcal{L})
                     = \deg(D) + 1 - g(X).\)
\notready
\end{theorem}

\begin{layman}
Take the dimensions of the two cohomology groups of a line bundle and
subtract: that's the \emph{Euler characteristic} of the bundle. The
theorem says this single number is determined by an embarrassingly simple
formula — the degree of the divisor (i.e., its total weight, possibly
negative), plus 1, minus the genus of the surface. No matter how
intricately the bundle is twisted, the alternating sum of its cohomology
dimensions collapses to that line. It's the same kind of magic as
Euler's classical \(V - E + F = 2\) for polyhedra: a wild combinatorial
quantity that's secretly determined by topology. Why bother? Combined
with Serre duality, this formula is exactly Riemann–Roch — the theorem
that lets us count how many independent meromorphic functions fit any
given budget of zeros and poles.
\end{layman}

\begin{theorem}[Classical input: Riemann-Roch (umbrella)]
\label{input:riemann-roch}
\uses{input:divisors,thm:serre-duality-rs,thm:euler-char-line-bundle}
\notready
For every divisor \(D\) on \(X\),
\[
  \ell(D)-\ell(K-D)=\deg(D)+1-g(X),
\]
where \(K\) is a canonical divisor and \(\ell(D)=\dim_{\C} L(D)\).
Combines the Euler-characteristic formula
(Theorem~\ref{thm:euler-char-line-bundle}) with Serre duality
(Theorem~\ref{thm:serre-duality-rs}).
\end{theorem}

\begin{layman}
We package the Riemann–Roch theorem as a single classical input.
Combining Serre duality (which converts hard cohomology into easy
cohomology) and the Euler-characteristic formula (which equates an
alternating sum to a topological constant) yields, for every divisor,
the famous identity: the dimension of functions fitting your budget,
minus the dimension of functions fitting the complementary budget,
equals degree-of-budget plus one minus genus. In plain words, the gap
between two sibling counting questions is a single number you can read
off from degree and genus. Why bother? Riemann–Roch is the workhorse
that turns abstract divisor theory into actual constructions: produce a
meromorphic function with this pole here, that zero there, and the
formula tells you whether it exists and how many such functions are
independent. Many of the proofs further down the dependency graph are
one-line corollaries of it.
\end{layman}

\begin{proposition}[Genus zero gives a degree-one meromorphic function]
\label{prop:genus-zero-degree-one-map}
\uses{input:riemann-roch}
If \(g(X)=0\), then for every \(p\in X\) there is a meromorphic function
\(f:X\to\CPone\) with exactly one simple pole at \(p\). In particular, \(f\)
has degree one.
\lean{JacobianChallenge.HolomorphicForms.homeomorphic_sphere_of_analyticGenus_eq_zero}
\leanok
\end{proposition}

\begin{layman}
Suppose the surface has genus zero — so the dimension of holomorphic
1-forms is zero. Pick any single point on the surface. Riemann–Roch,
applied to that one-point divisor, says the budget ``functions allowed
at most a simple pole there, holomorphic everywhere else'' has dimension
exactly \(2\). Two dimensions worth of functions means at least one of
them is nonconstant, and the constraint guarantees its only pole is the
one we chose. Such a function has exactly one pole on the surface —
which, viewed as a map to the Riemann sphere, has degree one (it's
one-to-one on a generic value). Why bother? This is the forward
direction of the genus-zero classification. Any genus-zero surface
admits a degree-one map to the sphere, and degree-one maps will turn out
to be honest isomorphisms — pinning the surface down as the sphere
itself.
\end{layman}

\begin{proof}
Apply Riemann-Roch to \(D=p\). Since \(\deg(p)=1\) and \(g(X)=0\),
\[
  \ell(p)-\ell(K-p)=2.
\]
The second term is zero because \(K-p\) has negative degree in genus zero.
Thus \(L(p)\) has dimension \(2\), so it contains a nonconstant meromorphic
function with at most a simple pole at \(p\). Such a function cannot have any
other pole and therefore defines a degree-one map to \(\CPone\).
\end{proof}

\subsection{Degree-one holomorphic maps to \texorpdfstring{\(\CPone\)}{CP1}}

\begin{definition}[Branched-cover degree of a nonconstant holomorphic map]
\label{def:branched-degree}
\uses{def:vanishing-order}
For a nonconstant holomorphic \(f:X\to Y\), the degree \(\deg(f)\) is
the cardinality, counted with multiplicity, of any generic fiber. Each
preimage \(p\in f^{-1}(q)\) contributes its ramification index
\(e_p(f)=\ord_p(f - f(p))\ge 1\); the sum is constant in \(q\) and
equals \(\deg(f)\).
\depends{Local power-series order at \(p\) (\texttt{analyticOrderAt});
constancy in the generic fiber from the open-mapping + isolated-zeros
machinery.}
\notready
\end{definition}

\begin{layman}
For a nonconstant holomorphic map between two compact Riemann surfaces,
the \emph{degree} counts how many times the map covers its target.
Pick a generic point downstairs and count its preimages, with
multiplicities at branch points where two or more sheets pinch together:
that count is the degree, and it's the same whichever generic target
point you choose. The multiplicity at a preimage is its
\emph{ramification index}, which measures how many sheets meet there. An
index of \(1\) means the map is a clean local homeomorphism nearby; an
index of \(2\) means two sheets pinch into one (like the square-root
function); higher indices mean more pinching. Why bother? Degree turns
holomorphic maps between surfaces into measurable things — the way
``2-to-1 covering'' or ``5-to-1 covering'' captures the structure. Most
of the classical theory of maps between Riemann surfaces (Riemann–Hurwitz,
the trace, push-pull) runs on this number.
\end{layman}

\begin{lemma}[Branch locus is finite]
\label{lem:branch-locus-finite}
\uses{def:branched-degree}
The set \(\{p\in X : e_p(f)\ge 2\}\) is finite.
\notready
\end{lemma}

\begin{layman}
The branch points of a map — places where two or more sheets pinch
together, so the ramification index jumps above \(1\) — can never form
an infinite cluster. Locally, ramification means the derivative of the
map vanishes. Derivatives of holomorphic gadgets are themselves
holomorphic, and on a compact surface the zero set of a nonzero
holomorphic gadget is always discrete and finite, by the same
identity-theorem-plus-compactness combo we saw for divisors. So branch
points come in tidy finite quantity. Why bother? Most theorems about
branched covers are easier to state and prove ``away from the branch
locus,'' and knowing that locus is finite guarantees we can always
extend conclusions across it by continuity — exactly how the trace of a
1-form will be defined later.
\end{layman}

\begin{proofsketch}
\(e_p(f)\ge 2\) iff the local derivative of \(f\) vanishes. The
derivative is itself meromorphic; its zero set is discrete by the
identity theorem, and finite by compactness.
\end{proofsketch}

\begin{lemma}[Degree-one forces no ramification]
\label{lem:degree-one-no-ramification}
\uses{def:branched-degree,lem:branch-locus-finite}
If \(\deg(f)=1\), then \(e_p(f)=1\) for every \(p\in X\), so \(f\) is
unramified.
\notready
\end{lemma}

\begin{layman}
If a holomorphic map between compact Riemann surfaces has degree one,
every fiber's ramification indices sum to one. Since each index is at
least one, the only way the total can equal one is if the fiber consists
of exactly one point with index exactly one. So no branching anywhere —
the map is everywhere a clean local homeomorphism. Why bother?
Degree-one maps are the candidate isomorphisms between Riemann surfaces.
Showing they have no branching is the first hurdle; the next hurdle
(local biholomorphism) and the final hurdle (global bijection) follow
from there. The whole genus-zero classification runs on this chain.
\end{layman}

\begin{proof}
At a generic fiber, the sum of ramification indices equals \(1\), so the
fiber has exactly one point with index \(1\). At a branch point \(p\),
the sum of indices over the fiber is also \(1\), but each index is
\(\ge 1\), so the fiber is a singleton \(\{p\}\) with \(e_p(f)=1\).
\end{proof}

\begin{theorem}[Local biholomorphism from unramified holomorphic]
\label{thm:local-biholo-unramified}
\uses{lem:degree-one-no-ramification}
An unramified nonconstant holomorphic map \(f:X\to Y\) is a local
biholomorphism: every \(p\in X\) has a neighborhood mapped
biholomorphically onto a neighborhood of \(f(p)\).
\depends{Mathlib's local inverse function theorem on \(\C\) plus the
fact that unramification means the local derivative is nonzero.}
\notready
\end{theorem}

\begin{layman}
Take a nonconstant holomorphic map that's unramified — meaning it never
pinches sheets together. Around every point, the map is a \emph{local
biholomorphism}: a small neighborhood of the source maps in a smooth,
invertible, holomorphic way onto a small neighborhood of the target.
The mechanism is the inverse function theorem from one-variable complex
analysis: unramified means the local derivative is nonzero, and a
nonzero derivative is exactly the condition for a holomorphic function
to have a holomorphic local inverse. Why bother? Locally, the map looks
like the identity (after a change of coordinates). Combined with
degree-one (every fiber a singleton), this will force the whole map to
be a global biholomorphism — the isomorphism we need to identify
genus-zero surfaces with the sphere.
\end{layman}

\begin{theorem}[Degree-one is bijective]
\label{thm:degree-one-bijective}
\uses{def:branched-degree,thm:local-biholo-unramified}
A degree-one holomorphic map \(f:X\to Y\) is bijective.
\notready
\end{theorem}

\begin{layman}
A degree-one holomorphic map between compact Riemann surfaces is a
bijection. \emph{Surjective}: a nonconstant holomorphic map between
compact surfaces is always onto — its image is open (open mapping
theorem) and closed (compactness), and a nonempty subset that's both
open and closed in a connected space is the whole thing. \emph{Injective}:
each fiber has size exactly one, by the no-ramification lemma. So the
map is both onto and one-to-one — a set-theoretic bijection. Why bother?
A continuous bijection between compact Hausdorff spaces is automatically
a homeomorphism (next theorem), and combined with the local
biholomorphism from above, that promotes our degree-one map to a full
biholomorphism between surfaces.
\end{layman}

\begin{proofsketch}
Surjective: a degree-\(d\) holomorphic map between compact Riemann
surfaces is surjective (the image is open by open-mapping and closed by
compactness). Injective: by
Lemma~\ref{lem:degree-one-no-ramification}, every fiber has exactly one
point with ramification index 1, hence cardinality 1.
\end{proofsketch}

\begin{theorem}[Compact-Hausdorff bijective continuous map is a homeomorphism]
\label{thm:compact-bijection-homeo}
A continuous bijection between compact Hausdorff spaces is a
homeomorphism.
\depends{Mathlib's \texttt{Continuous.homeoOfEquivCompactToT2}
or analogous topology fact (PRESENT).}
\lean{Continuous.homeoOfEquivCompactToT2}
\leanok\mathlibok
\end{theorem}

\begin{layman}
A purely topological gem: any continuous one-to-one onto map from one
compact Hausdorff space to another is automatically a homeomorphism —
its inverse is continuous for free, no extra checking required. The
reason is a chain of clean implications. Closed subsets of a compact
space are themselves compact. Compact subsets of a Hausdorff space are
closed. So the map sends closed sets to closed sets, which is exactly
continuity of the inverse. Why bother? Without it we'd have to manually
verify that the inverse is continuous everywhere, which on a curvy
surface is fiddly. With it, going from ``continuous bijection'' to
``isomorphism of topological spaces'' is one line. Mathlib already has
this packaged.
\end{layman}

\begin{theorem}[Classical input: Degree-one maps are isomorphisms (umbrella)]
\label{input:degree-one-isomorphism}
\uses{thm:degree-one-bijective,thm:local-biholo-unramified,thm:compact-bijection-homeo}
\notready
A nonconstant holomorphic map \(f:X\to\CPone\) of degree one is a
biholomorphism.
\end{theorem}

\begin{layman}
We package the chain ``degree-one nonconstant holomorphic map between
compact Riemann surfaces is a biholomorphism'' as a single classical
input. It bundles three steps: degree one means no ramification; no
ramification means a local biholomorphism everywhere; and a continuous
bijection between compact Hausdorff spaces is a homeomorphism — together
giving a global holomorphic isomorphism. Why bother? Combined with the
genus-zero existence proposition (genus zero gives a degree-one map to
the sphere), this umbrella delivers the forward direction of the
genus-zero classification: any genus-zero compact Riemann surface is
\emph{biholomorphic} to the Riemann sphere, hence in particular
homeomorphic to the topological sphere. That's the anti-hack
``genus zero iff homeomorphic to sphere'' baked into the challenge
statement.
\end{layman}

\begin{proof}[Proof of Theorem~\ref{thm:genus-zero-classification}]
If \(g(X)=0\), Proposition~\ref{prop:genus-zero-degree-one-map} and
Input~\ref{input:degree-one-isomorphism} identify \(X\) biholomorphically,
hence homeomorphically, with \(\CPone\), whose underlying topological space is
\(\Sphere\).

Conversely, if \(X\) is homeomorphic to \(\Sphere\), the topological genus is
zero. The comparison theorem between analytic genus
\(\dim_{\C}H^{0}(X,\Omega^{1}_{X})\) and topological genus gives \(g(X)=0\).
\end{proof}

\begin{formalizationnote}
The current Lean target splits this into the two directions in
\code{Jacobian/HolomorphicForms/GenusZeroClassification.lean}. The forward
direction needs Riemann-Roch, meromorphic functions, and degree-one map
classification. The reverse direction needs comparison of analytic and
topological genus.
\end{formalizationnote}
