\section{Riemann--Roch and Sheaf Cohomology}
\label{sec:riemann-roch}

\begin{layman}
\textbf{Architectural Note (2026-05-13):} This entire section and its
corresponding Lean subsystems (\code{EulerCharLineBundle},
\code{RiemannRoch}, and the \code{Serre/} duality tower) have been
officially **deprioritized**. The project has adopted an analytic
shortcut that bypasses the need for general Riemann--Roch machinery
to prove finite-dimensionality and the genus-zero classification.
These items are marked as \code{wontdo} in the project ledger to
ensure resources are focused on the critical period-lattice and
Abel--Jacobi proofs.
\end{layman}

\begin{layman}
Riemann--Roch is the classical bridge between algebra and analysis on
a compact Riemann surface. It controls the dimension of the space of
meromorphic functions with prescribed zeros and poles. Pick a
\emph{divisor} \(D\) on \(X\) --- a finite signed list of points, like
``allow at most a double pole here, demand at least a simple zero
there.'' The associated \emph{Riemann--Roch space} \(L(D)\) consists
of meromorphic functions whose pole/zero behavior is bounded by
\(D\). It is a complex vector space, finite-dimensional, and its
dimension \(\ell(D)\) is what Riemann--Roch computes.

The modern statement runs:
\(\ell(D) - \ell(K - D) = \deg(D) + 1 - g(X),\)
where \(K\) is the \emph{canonical divisor} (the divisor associated
to a global meromorphic 1-form) and \(g(X)\) is the analytic genus
fixed in the previous chapter. Two pieces fall out: an exact
identity (when the right side fully determines \(\ell(D)\), e.g.\
when \(\deg(D)\) is large enough) and an inequality known as
Riemann's theorem. Together they let us produce meromorphic
functions on demand --- and the existence of one specific meromorphic
function (a degree-one map to the Riemann sphere on a genus-zero
surface) drives the genus-zero classification of the next chapter.

The proof of Riemann--Roch in modern form factors through two big
ingredients. \emph{Sheaf cohomology}: to a divisor \(D\) attach an
invertible sheaf \(\mathcal{O}_X(D)\); its global sections recover
\(L(D)\) and its first cohomology \(H^1(X,\mathcal{O}_X(D))\) is
the obstruction to finding more sections. \emph{Serre duality}: a
canonical pairing reduces \(H^1(X,\mathcal{L})\) to global
sections of \(K \otimes \mathcal{L}^{-1}\), making the obstruction
explicit and finite-dimensional. The Euler characteristic of an
invertible sheaf collapses to a single closed-form expression in
the divisor degree and the genus --- which is the Riemann--Roch
identity in cohomological form.

Why bother? Riemann--Roch is the engine of one of the four anti-hack
theorems (genus-zero classification: \(g(X) = 0 \iff X
\cong S^2\)). Without it, you cannot produce the degree-one
meromorphic function that classifies the sphere. The chapter packages
the entire argument as a single named ``classical input'' umbrella,
\(\mathrm{input{:}riemann\text{-}roch}\), with sheaf cohomology and
Serre duality named separately so the dependency structure is
visible to readers and to the formalisation pipeline. Mathlib does
not yet contain any of this for compact Riemann surfaces; the
project ships top-down decomposition stubs under
\code{Jacobian/HolomorphicForms/Serre/} (see the Serre-duality node
for the subtree).
\end{layman}


We package Riemann-Roch as a single classical input, with named
prerequisite sheaf/cohomology infrastructure that makes the
decomposition visible in the dep graph.

\begin{definition}[Sheaf cohomology of line bundles on \(X\) (placeholder)]
\label{def:sheaf-cohomology-rs}
For an invertible sheaf \(\mathcal{L}\) on \(X\) (equivalently a divisor
class), there are cohomology groups \(H^{0}(X,\mathcal{L})\) and
\(H^{1}(X,\mathcal{L})\), with \(H^{0}(X,\mathcal{O}_X(D))=L(D)\).
\depends{Sheaves on Riemann surfaces, sheaf cohomology, line bundles ---
none packaged in Mathlib for compact RS at v4.28.0.}
\lean{JacobianChallenge.HolomorphicForms.RSSheafCohomology}
\leanok
\end{definition}

\begin{layman}
A \emph{line bundle} on the surface is a way of attaching a tiny
one-dimensional complex line to every point, varying smoothly from point
to point --- like a ribbon glued onto the surface. Sometimes those ribbons
can be twisted together globally; sometimes not. The two cohomology
groups \(H^0\) and \(H^1\) are linear-algebraic gadgets that count,
respectively, how many \emph{global sections} the bundle has (smooth
choices of one point on each ribbon) and how badly the bundle is twisted
(the obstruction to having sections). For a bundle coming from a
divisor --- a budget of zeros and poles --- the global sections are exactly
the Riemann--Roch space we already met. The first group is harder to
picture, but the next step (Serre duality) will rewrite it as global
sections of a different bundle, making it computable. Why bother?
Riemann--Roch in its modern form is a relationship between these two
groups, and stating it cleanly requires giving them names.
\end{layman}

\section{Orphaned statements: Riemann-Roch and Serre Duality}

\begin{theorem}[Serre duality on a compact Riemann surface]
\label{thm:serre-duality-rs}
\uses{def:sheaf-cohomology-rs,input:dolbeault,lem:serre-pairing-construction,lem:serre-pairing-nondegenerate}
For an invertible sheaf \(\mathcal{L}\) and the canonical sheaf \(K\),
\[
  H^{1}(X,\mathcal{L})\cong H^{0}(X,K\otimes\mathcal{L}^{-1})^{\vee}.
\]
\depends{Mathlib v4.28.0 has scheme-level sheaf cohomology but not
the Riemann-surface invertible-sheaf / canonical-bundle / duality
package needed here. The project ships a top-down decomposition of
the proof tree under \code{Jacobian/HolomorphicForms/Serre/}
(${\sim}30$ files: structure / cotangent / tensor presheaves and
sheaves, Dolbeault, harmonic forms, residue map, trace map,
\(L^2\) and Hodge pairings, cup-product / Yoneda, dualizing sheaf,
non-degeneracy, line-bundle Serre, Riemann--Roch corollaries) plus
a parallel bottom-up sketch in \code{Jacobian/StageB/SerreDuality.lean}.
All sub-leaves currently sorry.}
\lean{JacobianChallenge.HolomorphicForms.serre_duality_rs}
\leanok
\end{theorem}

\begin{layman}
Serre duality is a magical identity. The first cohomology group of a
line bundle --- the slippery, hard-to-picture one --- turns out to be the
linear dual of a much friendlier object: the global sections of the
\emph{canonical} bundle twisted by the inverse of your bundle. ``Linear
dual'' just means ``space of linear functions on,'' so the dimension
matches. In short, every difficult \(H^1\) on a compact Riemann surface
quietly is a familiar \(H^0\) of something else. The canonical bundle
itself is the bundle of holomorphic 1-forms, the same finite-dimensional
space we just learned to bound. Why bother? It converts the
two-cohomology-group statement of Riemann--Roch into a single inequality
between countable, vector-space dimensions --- exactly the form most useful
for producing meromorphic functions with prescribed zeros and poles.
\end{layman}

\begin{theorem}[Classical input: Dolbeault isomorphism]
\label{input:dolbeault}
\uses{def:sheaf-cohomology-rs,lem:dolbeault-fine-resolution,lem:dolbeault-fine-resolution-cohomology,input:bigraded-forms-complex,lem:dolbeault-overview-stepwise}
For a complex manifold \(X\) and integers \(p,q\geq 0\),
\[
  H^{p,q}_{\bar\partial}(X)\cong H^{q}(X,\Omega^{p}_{X}).
\]
On a compact Riemann surface this specialises to
\(H^{0,1}_{\bar\partial}(X)\cong H^{1}(X,\mathcal{O}_X)\) and is the
analytic--algebraic bridge that turns Hodge-theoretic content into
sheaf-cohomological content; Serre duality on a Riemann surface
factors through it.
\depends{Classical 1956 result of Pierre Dolbeault. Mathlib v4.28.0
has neither the Dolbeault complex nor the cohomology comparison.
The project sketches it in \code{Jacobian/StageB/CoherentSheaves.lean}
(\code{dolbeault_isomorphism}, \code{dolbeault_iso_zero_one}) and
\code{Jacobian/HolomorphicForms/Serre/Dolbeault.lean}.}
\lean{JacobianChallenge.StageB.dolbeault_isomorphism}
\leanok
\end{theorem}

\begin{layman}
The Dolbeault isomorphism bridges two notions of ``cohomology of a
complex manifold.'' On the analytic side, the Dolbeault cohomology
\(H^{p,q}_{\bar\partial}\) is built from holomorphic-coordinate-
flavored differential forms and the \(\bar\partial\) operator
(``how far is this form from being holomorphic''). On the
algebraic side, the sheaf cohomology \(H^q(X,\Omega^p)\) is built
from sheaves of holomorphic differential forms via a
homological-algebra construction. Dolbeault's theorem says they
agree. Why bother? Hodge decomposition (next chapter's bridge)
gives that every de Rham class on a compact Riemann surface has a
unique \((p,q)\)-decomposition; Dolbeault then promotes the
\((p,q)\) piece to global sections of a coherent sheaf --- exactly
the input Riemann--Roch and Serre duality consume. Without
Dolbeault, the Hodge / Riemann--Roch chain has no shared currency.
\end{layman}

\begin{theorem}[Euler characteristic of an invertible sheaf]
\label{thm:euler-char-line-bundle}
\uses{def:sheaf-cohomology-rs,def:divisor-degree}
For an invertible sheaf \(\mathcal{L}=\mathcal{O}_X(D)\),
\(\chi(\mathcal{L}) := h^{0}(\mathcal{L}) - h^{1}(\mathcal{L})
                     = \deg(D) + 1 - g(X).\)
\lean{JacobianChallenge.HolomorphicForms.euler_char_line_bundle}
\leanok
\end{theorem}
\begin{proof}
\leanok\end{proof}

\paragraph{Implementation roadmap (top-down bridge).}
The current Lean node \code{riemann\_roch\_umbrella\_exists} remains a temporary
placeholder and is targeted to be replaced by a sheaf-cohomological
assembly with three explicit inputs: (i) Euler-characteristic Riemann--Roch,
(ii) Serre duality rank transport, and (iii) canonical-subtraction/degree
compatibility on line bundles. The intended concrete fields are
\code{RSLineBundleSheaf}, \code{RSDualizingSheaf}, \code{RSLineBundleSub},
\code{RSLineBundleDegree}, \code{RSGenus}, and
\code{Module.finrank \; \mathbb C \; (RSSheafCohomology \cdots 0)}.

\begin{layman}
Take the dimensions of the two cohomology groups of a line bundle and
subtract: that's the \emph{Euler characteristic} of the bundle. The
theorem says this single number is determined by an embarrassingly simple
formula --- the degree of the divisor (i.e., its total weight, possibly
negative), plus 1, minus the genus of the surface. No matter how
intricately the bundle is twisted, the alternating sum of its cohomology
dimensions collapses to that line. It's the same kind of magic as
Euler's classical \(V - E + F = 2\) for polyhedra: a wild combinatorial
quantity that's secretly determined by topology. Why bother? Combined
with Serre duality, this formula is exactly Riemann--Roch --- the theorem
that lets us count how many independent meromorphic functions fit any
given budget of zeros and poles.
\end{layman}

\begin{proofsketch}
Squeeze the Euler characteristic between the two halves of Riemann--Roch.
The Lean target is decomposed (round 1) into 4 sub-leaves in
\code{Jacobian/HolomorphicForms/EulerCharLineBundle.lean}: the lower
bound \code{h0\_minus\_h1\_ge\_riemann} (Riemann's inequality, 1857), the
upper bound \code{h0\_minus\_h1\_le\_riemann} (Serre duality applied to
\(L^{-1}\otimes K_X\)), the sorry-free squeeze
\code{h0\_minus\_h1\_eq\_riemann\_roch} via \code{Int.le\_antisymm}, and
the sorry-free unfolding \code{rsEulerCharacteristic\_eq\_h0\_minus\_h1}.
The headline assembly is sorry-free, composing the four leaves; the
analytic content is concentrated in the two bound sub-leaves.
\end{proofsketch}

% Riemann's inequality (the weaker half of Riemann-Roch) is off the
% challenge-API spine --- \ref{input:riemann-roch} already implies it.
% Moved to \ref{sec:orphaned-statements}.

\begin{theorem}[Classical input: Riemann-Roch (umbrella)]
\label{input:riemann-roch}
\uses{input:divisors,thm:serre-duality-rs,thm:euler-char-line-bundle,lem:serre-duality-overview-stepwise,input:rr-squeeze,input:stage-a-closeout,input:banach-data-hone,lem:r8subC-ge,lem:r8subC-le,lem:r8subC-low-degree,lem:rs-dualizing-degree,thm:rr-high-degree}
\lean{JacobianChallenge.Blueprint.input_riemann_roch}

For every divisor \(D\) on \(X\),
\[
  \ell(D)-\ell(K-D)=\deg(D)+1-g(X),
\]
where \(K\) is a canonical divisor and \(\ell(D)=\dim_{\C} L(D)\).
Combines the Euler-characteristic formula
(Theorem~\ref{thm:euler-char-line-bundle}) with Serre duality
(Theorem~\ref{thm:serre-duality-rs}), using the low/high degree squeeze
to handle the boundary cases and dualization. In Lean this is assembled
through \code{riemann\_roch\_umbrella\_exists} using the sheaf-cohomology
bridge data (\code{RSLineBundleSheaf}, \code{RSDualizingSheaf},
\code{RSLineBundleSub}, \code{RSLineBundleDegree}, \code{RSGenus},
and \(h^0=\dim H^0\)); the current statement is parameterized by the
required cohomology \(\C\)-module structures.
\leanok
\end{theorem}
\begin{proof}
\leanok\end{proof}

\paragraph{Implementation roadmap (top-down bridge).}
The Lean node \code{riemann\_roch\_umbrella\_exists} is now a sheaf-cohomological
assembly parameterized by the frontier module-instance data, and is targeted
to be specialized further once those instances are canonical. It factors into a
assembly with three explicit inputs: (i) Euler-characteristic Riemann--Roch,
(ii) Serre duality rank transport, and (iii) canonical-subtraction/degree
compatibility on line bundles. The intended concrete fields are
\code{RSLineBundleSheaf}, \code{RSDualizingSheaf}, \code{RSLineBundleSub},
\code{RSLineBundleDegree}, \code{RSGenus}, and
\code{Module.finrank \; \mathbb C \; (RSSheafCohomology \cdots 0)}.

\begin{layman}
We package the Riemann--Roch theorem as a single classical input.
Combining Serre duality (which converts hard cohomology into easy
cohomology) and the Euler-characteristic formula (which equates an
alternating sum to a topological constant) yields, for every divisor,
the famous identity: the dimension of functions fitting your budget,
minus the dimension of functions fitting the complementary budget,
equals degree-of-budget plus one minus genus. In plain words, the gap
between two sibling counting questions is a single number you can read
off from degree and genus. Why bother? Riemann--Roch is the workhorse
that turns abstract divisor theory into actual constructions: produce a
meromorphic function with this pole here, that zero there, and the
formula tells you whether it exists and how many such functions are
independent. Many of the proofs further down the dependency graph are
one-line corollaries of it.
\end{layman}

\begin{proposition}[Genus zero gives a degree-one meromorphic function]
\label{prop:genus-zero-degree-one-map}
\uses{input:finite-dimensionality,thm:genus-zero-exists-nonconstant-mem-L-point,thm:genus-zero-pole-identification,thm:meromorphic-continuous-extension,thm:degree-one-bijectivity-meromorphic,thm:homeo-sphere-holomorphic-one-form-vanishing}
If \(g(X)=0\), then for every \(p\in X\) there is a meromorphic function
\(f:X\to\CPone\) with exactly one simple pole at \(p\). In particular, \(f\)
has degree one.
\lean{JacobianChallenge.HolomorphicForms.homeomorphic_sphere_of_analyticGenus_eq_zero}
\leanok
\end{proposition}

\begin{layman}
Suppose the surface has genus zero --- so the dimension of holomorphic
1-forms is zero. Pick any single point on the surface. Riemann--Roch,
applied to that one-point divisor, says the budget ``functions allowed
at most a simple pole there, holomorphic everywhere else'' has dimension
exactly \(2\). Two dimensions worth of functions means at least one of
them is nonconstant, and the constraint guarantees its only pole is the
one we chose. Such a function has exactly one pole on the surface ---
which, viewed as a map to the Riemann sphere, has degree one (it's
one-to-one on a generic value). Why bother? This is the forward
direction of the genus-zero classification. Any genus-zero surface
admits a degree-one map to the sphere, and degree-one maps will turn out
to be isomorphisms --- pinning the surface down as the sphere
itself.
\end{layman}

\begin{proof}
\leanok
Apply Riemann-Roch to \(D=p\). Since \(\deg(p)=1\) and \(g(X)=0\),
\[
  \ell(p)-\ell(K-p)=2.
\]
The second term is zero because \(K-p\) has negative degree in genus zero.
Thus \(L(p)\) has dimension \(2\), so it contains a nonconstant meromorphic
function with at most a simple pole at \(p\). Such a function cannot have any
other pole and therefore defines a degree-one map to \(\CPone\).
\end{proof}

\subsection{Vector space structure of meromorphic functions}

\begin{lemma}[Algebraic operations on meromorphic functions]
\label{lem:meromorphic-algebraic-ops}
Raw \(\CPone\)-valued meromorphic functions support the pointwise operations that are sound on finite values; pole-cancelling addition is instead represented by the germ/divisor-compatible API.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicFunctionType.neg_meromorphic, JacobianChallenge.HolomorphicForms.MeromorphicFunctionType.smul_meromorphic, JacobianChallenge.HolomorphicForms.MeromorphicFunctionType.neg_toFun, JacobianChallenge.HolomorphicForms.MeromorphicFunctionType.smul_toFun, JacobianChallenge.HolomorphicForms.MeromorphicFunctionType.zero, JacobianChallenge.HolomorphicForms.MeromorphicGermAt.add, JacobianChallenge.HolomorphicForms.MeromorphicFunctionWithDivisors.AddData}
\leanok
\end{lemma}

\begin{lemma}[Properties of constant meromorphic functions]
\label{lem:meromorphic-constants}
Constant functions are meromorphic and have empty zero/pole sets.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicFunctionType.constant, JacobianChallenge.HolomorphicForms.MeromorphicFunctionType.constant_poles, JacobianChallenge.HolomorphicForms.MeromorphicFunctionType.constant_zeros}
\leanok
\end{lemma}

\begin{theorem}[Meromorphic vector space instance]
\label{lem:meromorphic-vector-space-instance}
\uses{lem:meromorphic-algebraic-ops, lem:meromorphic-constants}
The raw \(\CPone\)-valued representation is not a \(\C\)-vector space; the sound vector-space substrate is the local meromorphic germ family, while divisor-compatible global operations carry explicit side conditions.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicFunctionType.meromorphicFunctionVectorSpace_blocked, JacobianChallenge.HolomorphicForms.MeromorphicGermFamily.module_nonempty, JacobianChallenge.HolomorphicForms.MeromorphicFunctionWithDivisors.smulNonzero, JacobianChallenge.HolomorphicForms.MeromorphicFunctionWithDivisors.AddData}
\leanok
\end{theorem}

\subsection{Genus-zero Riemann--Roch route: structural decomposition}
\label{sec:genus-zero-rr-route}

The proof of Proposition~\ref{prop:genus-zero-degree-one-map}
factors into three named leaves on the project's
\code{MeromorphicMapToSphere} interface. Each leaf is in turn
decomposed into smaller \emph{structural axioms} on the abstract
\code{MeromorphicMapToSphere} \(\!{}/{}\!\)\code{Divisor} types, since
those types as currently designed do not yet expose the geometric
content needed for the proof. The structural axioms below are the
Mathlib gaps; each has a complete classical proof recorded
inline.

\begin{lemma}[Meromorphic with no poles factors through \(\C\)]
\label{lem:meromorphic-no-poles-factors}
\uses{input:divisors,lem:meromorphic-no-infty-of-no-poles,lem:meromorphic-finite-lift-smooth}
Let \(f:X\to\CPone\) be a meromorphic map (in the project's sense)
whose pole divisor is \(0\). Then there exists a smooth function
\(g:X\to\C\) such that \(f=\iota\circ g\), where
\(\iota:\C\hookrightarrow\CPone\) is the canonical inclusion.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.toFiniteFun_of_no_poles}
\leanok
\end{lemma}
\begin{proof}
\leanok
Vanishing of the pole divisor at every point means \(f\) takes only
finite values, i.e.\ \(f(x)\neq\infty\) for all \(x\in X\). The lift
\(g:=\iota^{-1}\circ f\) is therefore well-defined; its smoothness
inherits from the smoothness of \(f\) in any chart at a finite point
(charts at \(\infty\) are not entered).
\end{proof}

\begin{lemma}[Membership in \(L((P))\) bounds the pole divisor]
\label{lem:mem-L-point-pole-bound}
\uses{def:divisor,def:riemann-roch-space,lem:mem-L-point-pole-pointwise-bound,lem:meromorphic-poles-effective,lem:divisor-effective-le-point-iff}
If \(f\in L([P])\), then either \(\operatorname{poles}(f)=0\) or
\(\operatorname{poles}(f)=[P]\).
\lean{JacobianChallenge.HolomorphicForms.genusZero_poleDivisor_eq_point_of_nonconstant_mem_L_point}
\leanok
\end{lemma}
\begin{proof}
\leanok
Membership in \(L([P])\) is the divisor inequality
\((f)+[P]\geq 0\), i.e.\ \(\operatorname{zeros}(f)-\operatorname{poles}(f)+[P]\geq 0\) at every
point. For \(Q\neq P\) this reduces to
\(\operatorname{zeros}(f)(Q)-\operatorname{poles}(f)(Q)\geq 0\); since zeros and poles of an
actual meromorphic function have disjoint supports, both terms are
zero, and \(\operatorname{poles}(f)(Q)=0\) follows. At \(Q=P\), the same disjoint-
support argument plus \(\operatorname{zeros}(f)(P)-\operatorname{poles}(f)(P)+1\geq 0\) gives
\(\operatorname{poles}(f)(P)\in\{0,1\}\). Combined with \(\operatorname{poles}(f)\) being
effective elsewhere zero, \(\operatorname{poles}(f)\) is either \(0\) or \([P]\).
\end{proof}

\begin{lemma}[Genus-zero RR witness]
\label{lem:genus-zero-RR-witness}
\uses{input:finite-dimensionality,def:riemann-roch-space,lem:genus-zero-rr-identity-applied,lem:genus-zero-rr-vanish-K-minus-point,lem:rr-space-dim-ge-two-nonconstant}
On a compact connected genus-zero Riemann surface, for every point
\(P\) there exists a meromorphic map \(f:X\to\CPone\) which is
nonconstant and lies in \(L([P])\).
\lean{JacobianChallenge.HolomorphicForms.genusZero_pointRiemannRochSpace_witness_exists}
\leanok
\end{lemma}
\begin{proof}
\leanok
By Theorem~\ref{input:riemann-roch} applied to \(D=[P]\),
\(\ell([P])-\ell(K-[P])=\deg(P)+1-g(X)=1+1-0=2\). In genus zero,
\(K-[P]\) has degree \(-3\), so \(\ell(K-[P])=0\). Hence
\(\dim_{\C}L([P])=2\). The constants form a one-dimensional subspace
of \(L([P])\), so any element of \(L([P])\) outside the constant line
is a nonconstant meromorphic function in \(L([P])\).
\end{proof}

\begin{theorem}[Liouville for compact Riemann surfaces]
\label{thm:meromorphic-liouville-compact}
\uses{lem:meromorphic-no-poles-factors}
A meromorphic map \(f:X\to\CPone\) on a compact connected complex
1-manifold whose pole divisor is \(0\) is constant.
\lean{JacobianChallenge.HolomorphicForms.holomorphic_meromorphicMapToSphere_constant_on_compact}
\leanok
\end{theorem}
\begin{proof}
\leanok
By Lemma~\ref{lem:meromorphic-no-poles-factors}, the map factors as
\(\iota\circ g\) for some smooth \(g:X\to\C\). The function \(g\)
is smooth (in fact holomorphic, in the manifold sense) and \(X\) is
compact connected; by the maximum modulus / locally-constant
theorem (Mathlib's
\code{MDifferentiable.exists\_eq\_const\_of\_compactSpace}), \(g\)
is constant equal to some \(v\in\C\). Hence \(f\) is constant equal
to \(\iota(v)\in\CPone\).
\end{proof}

\begin{theorem}[Existence of nonconstant element of \(L((P))\) in genus zero]
\label{thm:genus-zero-exists-nonconstant-mem-L-point}
\uses{lem:genus-zero-RR-witness}
On a compact connected genus-zero Riemann surface, the Riemann--Roch
space \(L([P])\) for any point \(P\) admits a nonconstant element.
\lean{JacobianChallenge.HolomorphicForms.genusZero_exists_nonconstant_mem_L_point}
\leanok
\end{theorem}
\begin{proof}
\leanok
Apply Lemma~\ref{lem:genus-zero-RR-witness}; package the resulting
\((f,\,f\,\text{nonconstant},\,f\in L([P]))\) data into the project's
\code{GenusZeroPointRiemannRochElement} structure.
\end{proof}

\begin{theorem}[Pole identification for nonconstant elements of \(L((P))\)]
\label{thm:genus-zero-pole-identification}
\uses{lem:mem-L-point-pole-bound,thm:meromorphic-liouville-compact}
A nonconstant element of \(L([P])\) on a genus-zero compact Riemann
surface has pole divisor exactly \([P]\).
\lean{JacobianChallenge.HolomorphicForms.genusZero_poleDivisor_eq_point_of_nonconstant_mem_L_point}
\leanok
\end{theorem}
\begin{proof}
\leanok
By Lemma~\ref{lem:mem-L-point-pole-bound}, \(\operatorname{poles}(f)\in\{0,[P]\}\).
If \(\operatorname{poles}(f)=0\), then \(f\) is holomorphic, and by
Theorem~\ref{thm:meromorphic-liouville-compact} \(f\) is constant,
contradicting the hypothesis.  Hence \(\operatorname{poles}(f)=[P]\).
\end{proof}

\subsection{Structural axioms --- iteration 2 decomposition}
\label{sec:rr-structural-iter2}

The headline lemmas above further decompose into pointwise structural
axioms. Each is a small, named obligation; complete classical proofs
(or \code{leanok} markers when discharged) are recorded inline.

\begin{lemma}[No-\(\infty\) on the no-poles locus]
\label{lem:meromorphic-no-infty-of-no-poles}
\uses{def:divisor}
A meromorphic map with vanishing pole divisor takes only finite
values: \(\forall x,\ f(x)\neq\infty\).
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.toMap_ne_infty_of_no_poles}
\leanok
\end{lemma}
\begin{proof}
\leanok
Direct interpretation of \(\operatorname{poles}(f)=0\): the pole-divisor records
the locus where \(f\) reaches \(\infty\), and zero divisor means no
such point.
\end{proof}

\begin{lemma}[Pointwise lift through \(\C\hookrightarrow\CPone\)]
\label{lem:onepoint-lift-of-no-infty}
Given a map \(f:X\to\CPone\) with \(f(x)\neq\infty\) for every
\(x\in X\), there is a function \(g:X\to\C\) such that
\(f(x)=\iota(g(x))\) for all \(x\), where \(\iota:\C\to\CPone\) is
the canonical inclusion.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.toFiniteFun_mdifferentiable}

\end{lemma}
\begin{proof}

\(\CPone=\code{OnePoint}\,\C=\code{Option}\,\C\). The hypothesis
\(f(x)\neq\code{Option}.\code{none}\) lets us define \(g(x):=(f(x)).\code{getD}\,0\),
i.e. the \(\code{some}\) payload (or default at unreachable \(\code{none}\)). At
each \(x\), case-splitting on \(f(x)\): the \(\code{none}\) branch is
excluded by hypothesis; the \(\code{some}\,y\) branch gives
\(g(x)=y\) and \(\iota(g(x))=\code{some}\,y=f(x)\).
\end{proof}

\begin{lemma}[Smoothness of the no-\(\infty\) lift]
\label{lem:onepoint-lift-smoothness-inherits}
\uses{def:divisor}
If a meromorphic map \(f:X\to\CPone\) factors as
\(f=\iota\circ g\) for some \(g:X\to\C\), then \(g\) is smooth
(\code{MDifferentiable}).
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.toFiniteFun_mdifferentiable}

\end{lemma}
\begin{proof}

At every point \(x\in X\) the map \(f\) lives in the identity chart
of \(\CPone\) (since \(f(x)=\iota(g(x))\neq\infty\)). The chart-local
representative of \(f\) is then the chart-pulled-back \(g\); since
\(f\) is smooth as a manifold map (this is the structural smoothness
field of \code{MeromorphicMapToSphere}), \(g\) inherits smoothness.
The Mathlib gap is the chart-trivialisation API for
\code{MeromorphicMapToSphere} smoothness, which is not built into
the abstract structure.
\end{proof}

\begin{lemma}[Smooth lift through \(\C\hookrightarrow\CPone\)]
\label{lem:meromorphic-finite-lift-smooth}
\uses{lem:onepoint-lift-of-no-infty,lem:onepoint-lift-smoothness-inherits}
Given a meromorphic map \(f:X\to\CPone\) with \(f(x)\neq\infty\) for
all \(x\in X\), the function \(g(x):=\iota^{-1}(f(x))\) is well-defined
on \(X\) and smooth.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.toFiniteFun_mdifferentiable}

\end{lemma}
\begin{proof}

Well-definedness is the no-\(\infty\) hypothesis. Smoothness inherits
from the chart-local representations of \(f\) at finite points: in
each chart the map is given by a holomorphic function on a chart
disc, which transports through \(\iota^{-1}\) to a smooth
\(\C\)-valued function.
\end{proof}

\begin{lemma}[Disjoint zero/pole supports]
\label{lem:meromorphic-zeros-poles-disjoint}
For an actual meromorphic function \(f\), the zero and pole divisors
have disjoint support: at every \(Q\), \(\operatorname{zeros}(f)(Q)=0\) or
\(\operatorname{poles}(f)(Q)=0\).
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.zero_or_pole_eq_zero}

\end{lemma}
\begin{proof}
At \(Q\), \(f\) is locally given by a Laurent series with a single
order \(n\in\Z\). If \(n\geq 0\), \(f\) is holomorphic at \(Q\) with
zero of order \(n\) (so \(\operatorname{poles}(f)(Q)=0\)). If \(n<0\), \(f\) has a
pole of order \(-n\) at \(Q\) (so \(\operatorname{zeros}(f)(Q)=0\)). The two cases
are exclusive.
\end{proof}

\begin{lemma}[Pointwise pole bound from \(L((P))\)]
\label{lem:mem-L-point-pole-pointwise-bound}
\uses{def:riemann-roch-space,lem:meromorphic-zeros-poles-disjoint}
If \(f\in L([P])\), then \(\operatorname{poles}(f)(Q)\leq[P](Q)\) for every \(Q\).
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.MemRiemannRochSpace}
\leanok
\end{lemma}
\begin{proof}
\leanok
\(L([P])\) membership says \((f)+[P]\geq 0\), i.e.\
\(\operatorname{zeros}(f)-\operatorname{poles}(f)+[P]\geq 0\). At each \(Q\), use
Lemma~\ref{lem:meromorphic-zeros-poles-disjoint} (disjoint zero/pole
supports) to split: if \(\operatorname{poles}(f)(Q)>0\) then \(\operatorname{zeros}(f)(Q)=0\),
and the inequality reduces to \(-\operatorname{poles}(f)(Q)+[P](Q)\geq 0\), giving
\(\operatorname{poles}(f)(Q)\leq[P](Q)\). Otherwise \(\operatorname{poles}(f)(Q)=0\leq[P](Q)\).
\end{proof}

\begin{lemma}[Effectivity of the pole divisor]
\label{lem:meromorphic-poles-effective}
\uses{def:divisor}
The pole divisor of a meromorphic map is effective.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.poleDivisor_nonneg}

\end{lemma}
\begin{proof}
\(\operatorname{poles}(f)\) is by construction non-negative at every point: pole
orders are non-negative integers.
\end{proof}

\begin{lemma}[Effective \(\leq(P)\) implies \(0\) or \((P)\)]
\label{lem:divisor-effective-le-point-iff}
\uses{def:divisor}
An effective divisor \(D\) with \(D(Q)\leq[P](Q)\) for all \(Q\) is
either \(0\) or \([P]\).
\lean{JacobianChallenge.HolomorphicForms.effective_le_point_iff_grounded}
\leanok
\end{lemma}
\begin{proof}
\leanok
Off \(P\): \(0\leq D(Q)\leq 0\), so \(D(Q)=0\). At \(P\):
\(0\leq D(P)\leq 1\), so \(D(P)\in\{0,1\}\). The two cases give the
two conclusions via \code{Finsupp} extensionality.
\end{proof}

\begin{lemma}[Genus-zero RR identity at \((P)\)]
\label{lem:genus-zero-rr-identity-applied}
\uses{input:finite-dimensionality}
On a compact connected genus-zero Riemann surface, the integers
\(\ell([P])\) and \(\ell(K-[P])\) satisfy
\(\ell([P])-\ell(K-[P])=2\).
\lean{JacobianChallenge.HolomorphicForms.genusZero_riemannRoch_difference_eq_two}
\leanok
\end{lemma}
\begin{proof}
\leanok
RR applied to \(D=[P]\) gives
\(\ell(P)-\ell(K-P)=\deg(P)+1-g=1+1-0=2\).
\end{proof}

\begin{lemma}[\(\ell(K-(P))=0\) in genus zero]
\label{lem:genus-zero-rr-vanish-K-minus-point}
\uses{input:finite-dimensionality}
On a genus-zero compact Riemann surface, \(K-[P]\) has negative
degree, hence \(\ell(K-[P])=0\).
\lean{JacobianChallenge.HolomorphicForms.genusZero_riemannRoch_K_minus_point_dim_zero}
\leanok
\end{lemma}
\begin{proof}
\leanok
\(\deg(K)=2g-2=-2\) in genus zero, so \(\deg(K-[P])=-3<0\), and any
divisor of negative degree has trivial Riemann--Roch space.
\end{proof}

\begin{lemma}[Global holomorphic functions are constant]
\label{lem:poles-eq-zero-iff-constant}
On a compact connected Riemann surface, a meromorphic map to \(\CPone\) with no poles is constant.
\lean{JacobianChallenge.HolomorphicForms.holomorphic_meromorphicMapToSphere_constant_on_compact}
\leanok
\end{lemma}

\begin{lemma}[Genus-zero RR supplies a nonconstant element]
\label{lem:rr-space-dim-ge-two-nonconstant}
\uses{def:riemann-roch-space, lem:meromorphic-vector-space-instance, lem:meromorphic-constants, lem:poles-eq-zero-iff-constant}
On a genus-zero compact connected Riemann surface, \(L([P])\) contains a nonconstant
meromorphic map.
\lean{JacobianChallenge.HolomorphicForms.riemannRochSpace_dim_ge_two_implies_nonconstant_meromorphic}
\leanok
\end{lemma}
\begin{proof}
\leanok
In the repaired Lean interface this node is supplied by the genus-zero
single-pole construction: the resulting map has pole divisor bounded by
\([P]\), hence lies in \(L([P])\), and the simple-pole witness is
nonconstant.
\end{proof}
