\section{Branched Covers and the Genus-Zero Classification}
\label{sec:branched-covers-genus-zero}

\begin{layman}
A nonconstant holomorphic map between compact Riemann surfaces is
never just an injection — it is a \emph{branched covering}. Most
points in the target have the same finite number \(d\) of preimages
in the source; at finitely many \emph{branch points} the preimages
collide with multiplicity. The number \(d\) is the \emph{degree} of
the map, the basic numerical invariant of the cover. A degree-one
holomorphic map between compact Riemann surfaces — generic fibre is
a single point — is automatically a homeomorphism, and in fact a
biholomorphism: this is one of the chapter's punch lines and the
key step in the genus-zero classification.

The chapter begins by formalising what ``degree'' means. Each
preimage \(p\) of a base point \(q\) carries a \emph{ramification
index} \(e_p(f)\), the local-power-series order of \(f - f(p)\) at
\(p\). The fibre sum \(\sum_{p \in f^{-1}(q)} e_p(f)\) is the
weighted count of preimages; the weighted-fibre-sum-is-locally-
constant theorem then forces this count to be the same for every
\(q\) — that constant value is the degree. Showing local constancy
costs real work: the unramified locus is open, ramified points are
isolated and finite, the chart-local power series can be put in a
local conjugate-to-\(z^k\) normal form via a holomorphic \(k\)-th
root, and the weighted sum is locally constant on each side and
glues across.

With the degree definition in hand, the chapter develops the
infrastructure that pins down a degree-one map. At every unramified
point the map is locally a chart-to-chart inverse; the entire fibre
of a regular value is a singleton when degree is one; an unramified
nonconstant holomorphic map is a local biholomorphism; a degree-one
nonconstant holomorphic map between compact Riemann surfaces is a
homeomorphism. Combine with Riemann-Roch on a genus-zero surface
(producing a degree-one meromorphic function to the Riemann sphere)
and you get the first anti-hack theorem of the challenge:
\emph{analytic genus zero is equivalent to being homeomorphic to
the 2-sphere}. The chapter ends with that classification.

Why bother? The genus-zero classification is one of the four anti-
hack theorems pinned by \texttt{Jacobian/Challenge.lean}. It rules
out trivial fake constructions like \texttt{genus X := 0}: the
challenge demands that \texttt{genus X = 0} actually entails \(X\)
is the topological sphere. Reaching that conclusion goes through
exactly this chapter — branched degree, Riemann-Hurwitz, degree-one
classification, and the analytic-genus-zero \(\Rightarrow\)
sphere argument.
\end{layman}


\begin{definition}[Branched-cover degree of a nonconstant holomorphic map]
\label{def:branched-degree}
\uses{def:vanishing-order}
For a nonconstant holomorphic \(f:X\to Y\), the degree \(\deg(f)\) is
the cardinality, counted with multiplicity, of any generic fiber. Each
preimage \(p\in f^{-1}(q)\) contributes its ramification index
\(e_p(f)=\ord_p(f - f(p))\ge 1\); the sum is constant in \(q\) and
equals \(\deg(f)\).
\depends{Local power-series order at \(p\) (\texttt{analyticOrderAt});
constancy in \(q\) is the content of
\texttt{thm:branched-degree-well-defined}, decomposed into
\texttt{lem:branch-locus-finite},
\texttt{lem:local-inj-unramified},
\texttt{lem:local-kfold-ramified}, and
\texttt{lem:weighted-fiber-locally-constant}.}
\lean{JacobianChallenge.Blueprint.branchedDegree}
\leanok
\end{definition}

\begin{layman}
For a nonconstant holomorphic map between two compact Riemann surfaces,
the \emph{degree} counts how many times the map covers its target.
Pick a generic point downstairs and count its preimages, with
multiplicities at branch points where two or more sheets pinch together:
that count is the degree, and it's the same whichever generic target
point you choose. The multiplicity at a preimage is its
\emph{ramification index}, which measures how many sheets meet there. An
index of \(1\) means the map is a clean local homeomorphism nearby; an
index of \(2\) means two sheets pinch into one (like the square-root
function); higher indices mean more pinching. Why bother? Degree turns
holomorphic maps between surfaces into measurable things — the way
``2-to-1 covering'' or ``5-to-1 covering'' captures the structure. Most
of the classical theory of maps between Riemann surfaces (Riemann–Hurwitz,
the trace, push-pull) runs on this number.
\end{layman}

\begin{lemma}[Branch locus is finite]
\label{lem:branch-locus-finite}
\uses{def:branched-degree, lem:order-eq-one-iff-deriv-ne-zero,
lem:unramified-set-open, lem:ramified-isolated}
The set \(\{p\in X : e_p(f)\ge 2\}\) is finite.
\depends{Sub-sub-leaves: \texttt{lem:unramified-set-open} (the
unramified set is open) and \texttt{lem:ramified-isolated} (every
ramified point is isolated in the ramified set); assembly is
``closed-discrete subset of compact \(\Rightarrow\) finite''.}
\lean{JacobianChallenge.Blueprint.branch_locus_finite}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{lemma}[Unramified set is open]
\label{lem:unramified-set-open}
\uses{lem:order-eq-one-iff-deriv-ne-zero}
The set \(\{x\in X : e_x(f)=1\}\) is open in \(X\).
\depends{Continuity of the chart-local derivative plus the chart-pull
of the open condition \(\{(z) : g'(z)\ne 0\}\subseteq\C\).}
\lean{JacobianChallenge.Blueprint.isOpen_setOf_mapAnalyticOrderAt_eq_one}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{lemma}[Every ramified point is isolated]
\label{lem:ramified-isolated}
\uses{lem:order-eq-one-iff-deriv-ne-zero}
At a ramified point \(x\) (\(e_x(f)\ge 2\)), there is a punctured
neighborhood of \(x\) consisting entirely of unramified points.
\depends{Mathlib's \texttt{AnalyticAt.eventually\_ne} applied to the
chart-local derivative (which has order \(\ge k-1\ge 1\) at the chart
image of \(x\)) plus the common helper.}
\lean{JacobianChallenge.Blueprint.mapAnalyticOrderAt_isolated_at_ramified}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{layman}
The branch points of a map — places where two or more sheets pinch
together, so the ramification index jumps above \(1\) — can never form
an infinite cluster. Locally, ramification means the derivative of the
map vanishes. Derivatives of holomorphic gadgets are themselves
holomorphic, and on a compact surface the zero set of a nonzero
holomorphic gadget is always discrete and finite, by the same
identity-theorem-plus-compactness combo we saw for divisors. So branch
points come in tidy finite quantity. Why bother? Most theorems about
branched covers are easier to state and prove ``away from the branch
locus,'' and knowing that locus is finite guarantees we can always
extend conclusions across it by continuity — exactly how the trace of a
1-form will be defined later.
\end{layman}

\begin{proofsketch}
\(e_p(f)\ge 2\) iff the local derivative of \(f\) vanishes. The
derivative is itself meromorphic; its zero set is discrete by the
identity theorem, and finite by compactness.
\end{proofsketch}

\begin{lemma}[Local injectivity at an unramified point]
\label{lem:local-inj-unramified}
\uses{def:branched-degree, lem:order-eq-one-iff-deriv-ne-zero, lem:chart-local-inverse-unramified}
If \(e_x(f)=1\) at a point \(x\in X\), there is an open neighborhood
\(U\ni x\) and an open neighborhood \(V\ni f(x)\) such that for every
\(y\in V\), the set \(U\cap f^{-1}(y)\) is a singleton.
\depends{Sub-sub-leaves: \texttt{lem:order-eq-one-iff-deriv-ne-zero}
(common B1=A1 helper) and \texttt{lem:chart-local-inverse-unramified}
(B2, Mathlib's \texttt{AnalyticAt.localInverse}); assembly is chart
transport.}
\lean{JacobianChallenge.Blueprint.IsHolomorphicAt.exists_local_inj_of_unramified}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{lemma}[Order one iff chart-local derivative nonzero]
\label{lem:order-eq-one-iff-deriv-ne-zero}
\uses{def:branched-degree, def:vanishing-order}
The chart-local order \(e_x(f)=1\) iff the derivative
\((\chi\circ f\circ\varphi^{-1})'(\varphi(x))\ne 0\), where
\((\varphi,\chi)\) are the canonical charts at \(x\) and \(f(x)\).
\depends{Mathlib's
\texttt{AnalyticAt.analyticOrderAt\_sub\_eq\_one\_of\_deriv\_ne\_zero}
plus the
\texttt{analyticOrderNatAt}\(\,=1\) \(\iff\) \texttt{analyticOrderAt}\(\,=1\) characterisation.}
\lean{JacobianChallenge.Blueprint.mapAnalyticOrderAt_eq_one_iff_chartLocal_deriv_ne_zero}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{lemma}[Chart-local inverse at unramified]
\label{lem:chart-local-inverse-unramified}
\uses{lem:order-eq-one-iff-deriv-ne-zero}
At an unramified point \(x\), the chart-local presentation
\(\chi\circ f\circ\varphi^{-1}\) admits a holomorphic local inverse
near \(\chi(f(x))\).
\depends{\texttt{AnalyticAt.localInverse} from
\texttt{Mathlib/Analysis/Analytic/Inverse.lean}.}
\lean{JacobianChallenge.Blueprint.chartLocalAt_localInverse_of_unramified}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{layman}
At a point where the holomorphic map doesn't pinch sheets together
(ramification index \(1\)), the map is a clean local
homeomorphism: zoom in enough and you see a single sheet covering a
single small disk, with each downstairs point having a unique upstairs
preimage. Why bother? This is the building block for conservation of
the weighted fibre count off branch values: every unramified preimage
contributes exactly \(1\) to the count, and that count is locally
stable because nearby downstairs points have exactly the same
unique-preimage neighborhoods.
\end{layman}

\begin{proofsketch}
The chart-local power-series expansion at \(x\) is
\(f(t)=a\cdot t+O(t^2)\) with \(a\ne 0\), so the chart-local derivative
is nonzero at the chart image of \(x\). Apply the analytic inverse
function theorem for \(\C\to\C\) to get a chart-local inverse on a
neighborhood; transport back through the canonical charts on \(X\)
and \(Y\).
\end{proofsketch}

\begin{lemma}[Local power-series form at order \texorpdfstring{\(k\)}{k}]
\label{lem:chart-local-pow-mul}
\uses{def:branched-degree, def:vanishing-order}
If \(e_x(f)=k\ge 1\), the centred chart-local difference factors as
\((t-z_0)^k\cdot g(t)\) for some analytic \(g\) with \(g(z_0)\ne 0\),
where \(z_0\) is the chart image of \(x\).
\depends{Direct application of Mathlib's
\texttt{AnalyticAt.analyticOrderAt\_eq\_natCast}.}
\lean{JacobianChallenge.Blueprint.chartLocalAt_eq_pow_mul_of_order}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{lemma}[Holomorphic \texorpdfstring{\(k\)}{k}-th root]
\label{lem:analytic-kth-root}
\uses{lem:akr-r1}
If \(g\) is analytic at \(z_0\) with \(g(z_0)\ne 0\) and \(k\ge 1\),
there is an analytic \(h\) near \(z_0\) with \(h(z)^k=g(z)\) locally.
\depends{Holomorphic logarithm
(\texttt{Complex.analyticAt\_log} on a simply-connected nbhd of
\(g(z_0)\) avoiding \(0\)) plus \(\exp\) plus
\(h:=\exp((1/k)\cdot\log g)\).}
\lean{JacobianChallenge.Blueprint.analyticAt_kth_root_of_ne_zero}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{lemma}[Local \texorpdfstring{\(k\)}{k}-fold structure at a ramified point]
\label{lem:local-kfold-ramified}
\uses{def:branched-degree, def:vanishing-order,
lem:chart-local-pow-mul, lem:analytic-kth-root}
If \(e_x(f)=k\ge 1\), there is an open neighborhood \(U\ni x\) and an
open neighborhood \(V\ni f(x)\) such that for every \(y\in V\) with
\(y\ne f(x)\), the set \(U\cap f^{-1}(y)\) consists of exactly \(k\)
distinct unramified preimages.
\depends{Sub-sub-leaves: \texttt{lem:chart-local-pow-mul} (C1, local
power-series form) and \texttt{lem:analytic-kth-root} (C2,
holomorphic \(k\)-th root); assembly is the substitution
\(s=(t-z_0)\cdot h(t)\) flattening the local form to \(s\mapsto s^k\),
which has exactly \(k\) simple preimages of any nonzero target.}
\lean{JacobianChallenge.Blueprint.IsHolomorphicAt.exists_local_kfold_of_ramified}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{layman}
At a branch point of order \(k\), the map locally looks like
\(z\mapsto z^k\): the \(k\) sheets that meet at the branch point pull
apart as you move slightly away, becoming \(k\) distinct simple
preimages of any nearby target. This is what conserves the weighted
fibre count across branch values: the single ramified preimage with
weight \(k\) splits into \(k\) simple preimages, each with weight
\(1\), summing to \(k\) again.
\end{layman}

\begin{proofsketch}
Write \(f(t)=t^k\cdot g(t)\) in a chart at \(x\), with \(g(0)\ne 0\).
Choose a holomorphic \(k\)-th root \(g(t)^{1/k}\) (exists since \(g\)
is nonvanishing near \(0\)) and substitute \(s=t\cdot g(t)^{1/k}\) to
flatten the local form to \(f(s)=s^k\). The map \(s\mapsto s^k\) has
exactly \(k\) simple preimages of any nonzero point. Transport back
through charts.
\end{proofsketch}

\begin{lemma}[Properness of fibre below an open neighborhood]
\label{lem:proper-fiber-shrink}
\uses{lem:pfs-r1}
For a continuous map \(f\) from a compact source to a Hausdorff
target, and any open \(U\) containing \(f^{-1}(y_0)\), there is a
neighborhood \(V\) of \(y_0\) such that for every \(y\in V\),
\(f^{-1}(y)\subseteq U\).
\depends{\(U^c\) is closed-in-compact \(\Rightarrow\) compact; image \(f(U^c)\) is
compact \(\Rightarrow\) closed in \(T_2\); \(y_0\notin f(U^c)\); take
\(V:=f(U^c)^c\).}
\lean{JacobianChallenge.Blueprint.eventually_fiber_subset_of_compact_T2}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{lemma}[Weighted fibre count locally constant at a single point]
\label{lem:weighted-fiber-eventually-eq}
\uses{lem:local-inj-unramified, lem:local-kfold-ramified, lem:proper-fiber-shrink}
At every \(y_0\in Y\), there is a neighborhood \(V\ni y_0\) on which
the weighted fibre sum is constant equal to its value at \(y_0\).
\depends{Choose pairwise-disjoint open nbhds \(U_x\) around each
\(x\in f^{-1}(y_0)\) (T2 + finite); shrink each \(U_x\) so that
either \texttt{lem:local-inj-unramified} (if \(e_x=1\)) or
\texttt{lem:local-kfold-ramified} (if \(e_x\ge 2\)) applies, with an
associated \(V_x\); intersect with the neighborhood from
\texttt{lem:proper-fiber-shrink} to ensure all preimages of nearby
\(y\) lie in \(\bigcup U_x\); sum contributions.}
\lean{JacobianChallenge.Blueprint.weightedFiberSum_eventually_eq}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{lemma}[Weighted fibre count is locally constant]
\label{lem:weighted-fiber-locally-constant}
\uses{lem:weighted-fiber-eventually-eq}
For a nonconstant holomorphic \(f:X\to Y\) between a compact
preconnected complex \(1\)-manifold and a Hausdorff complex
\(1\)-manifold, the weighted fibre sum
\(y\mapsto\sum_{p\in f^{-1}(y)}e_p(f)\) is locally constant on \(Y\).
\depends{Direct corollary of
\texttt{lem:weighted-fiber-eventually-eq} (which holds at every
\(y_0\)) plus
\texttt{IsLocallyConstant.iff\_eventuallyEq} from Mathlib.}
\lean{JacobianChallenge.Blueprint.isHolomorphic_weightedFiberSum_isLocallyConstant}
\leanok
\end{lemma}
\begin{proof}\leanok\end{proof}

\begin{layman}
The weighted fibre count is the same for nearby downstairs points: at
each preimage, the local picture (either a single unramified sheet of
weight \(1\), or \(k\) simple sheets summing to \(k\), or one
ramified sheet of weight \(k\)) contributes the same amount whether
you're sitting exactly at the branch value or slightly displaced.
Stitching together all the preimages of a target point — there are
finitely many — and choosing disjoint neighborhoods around each, the
total weighted count is locally constant.
\end{layman}

\begin{theorem}[Branched degree is well-defined]
\label{thm:branched-degree-well-defined}
\uses{lem:weighted-fiber-locally-constant}
For a nonconstant holomorphic \(f:X\to Y\) between compact preconnected
complex \(1\)-manifolds, the weighted fibre sum is constant on \(Y\):
the same nonnegative integer \(\deg(f)\) is obtained at every base
point.
\depends{Local-constancy from
\texttt{lem:weighted-fiber-locally-constant} plus
\texttt{IsLocallyConstant.apply\_eq\_of\_preconnectedSpace} from
Mathlib (preconnected target \(\Rightarrow\) globally constant).}
\lean{JacobianChallenge.Blueprint.isHolomorphic_weightedFiberSum_const}
\leanok
\end{theorem}
\begin{proof}\leanok\end{proof}

\begin{layman}
Locally constant on a connected target means globally constant. So the
weighted fibre count assigns the same number — the degree — to every
target point. This is the proof that ``the degree of a holomorphic map''
is actually a single well-defined number, not a value that drifts as
you move around the target.
\end{layman}

\begin{lemma}[Degree-one forces no ramification]
\label{lem:degree-one-no-ramification}
\uses{def:branched-degree,lem:branch-locus-finite}
If \(\deg(f)=1\), then \(e_p(f)=1\) for every \(p\in X\), so \(f\) is
unramified.
\lean{JacobianChallenge.Blueprint.degree_one_no_ramification}
\leanok
\end{lemma}

\begin{layman}
If a holomorphic map between compact Riemann surfaces has degree one,
every fiber's ramification indices sum to one. Since each index is at
least one, the only way the total can equal one is if the fiber consists
of exactly one point with index exactly one. So no branching anywhere —
the map is everywhere a clean local homeomorphism. Why bother?
Degree-one maps are the candidate isomorphisms between Riemann surfaces.
Showing they have no branching is the first hurdle; the next hurdle
(local biholomorphism) and the final hurdle (global bijection) follow
from there. The whole genus-zero classification runs on this chain.
\end{layman}

\begin{proof}\leanok
At a generic fiber, the sum of ramification indices equals \(1\), so the
fiber has exactly one point with index \(1\). At a branch point \(p\),
the sum of indices over the fiber is also \(1\), but each index is
\(\ge 1\), so the fiber is a singleton \(\{p\}\) with \(e_p(f)=1\).
\end{proof}

\begin{theorem}[Local biholomorphism from unramified holomorphic]
\label{thm:local-biholo-unramified}
\uses{lem:degree-one-no-ramification}
An unramified nonconstant holomorphic map \(f:X\to Y\) is a local
biholomorphism: every \(p\in X\) has a neighborhood mapped
biholomorphically onto a neighborhood of \(f(p)\).
\depends{Mathlib's local inverse function theorem on \(\C\) plus the
fact that unramification means the local derivative is nonzero.}
\lean{JacobianChallenge.Blueprint.local_biholo_unramified}
\leanok
\end{theorem}
\begin{proof}\leanok\end{proof}

\begin{layman}
Take a nonconstant holomorphic map that's unramified — meaning it never
pinches sheets together. Around every point, the map is a \emph{local
biholomorphism}: a small neighborhood of the source maps in a smooth,
invertible, holomorphic way onto a small neighborhood of the target.
The mechanism is the inverse function theorem from one-variable complex
analysis: unramified means the local derivative is nonzero, and a
nonzero derivative is exactly the condition for a holomorphic function
to have a holomorphic local inverse. Why bother? Locally, the map looks
like the identity (after a change of coordinates). Combined with
degree-one (every fiber a singleton), this will force the whole map to
be a global biholomorphism — the isomorphism we need to identify
genus-zero surfaces with the sphere.
\end{layman}

\begin{theorem}[Degree-one is bijective]
\label{thm:degree-one-bijective}
\uses{def:branched-degree,thm:local-biholo-unramified}
A degree-one holomorphic map \(f:X\to Y\) is bijective.
\lean{JacobianChallenge.Blueprint.degree_one_bijective}
\leanok
\end{theorem}
\begin{proof}\leanok\end{proof}

\begin{layman}
A degree-one holomorphic map between compact Riemann surfaces is a
bijection. \emph{Surjective}: a nonconstant holomorphic map between
compact surfaces is always onto — its image is open (open mapping
theorem) and closed (compactness), and a nonempty subset that's both
open and closed in a connected space is the whole thing. \emph{Injective}:
each fiber has size exactly one, by the no-ramification lemma. So the
map is both onto and one-to-one — a set-theoretic bijection. Why bother?
A continuous bijection between compact Hausdorff spaces is automatically
a homeomorphism (next theorem), and combined with the local
biholomorphism from above, that promotes our degree-one map to a full
biholomorphism between surfaces.
\end{layman}

\begin{proofsketch}
Surjective: a degree-\(d\) holomorphic map between compact Riemann
surfaces is surjective (the image is open by open-mapping and closed by
compactness). Injective: by
Lemma~\ref{lem:degree-one-no-ramification}, every fiber has exactly one
point with ramification index 1, hence cardinality 1.
\end{proofsketch}

\begin{theorem}[Compact-Hausdorff bijective continuous map is a homeomorphism]
\label{thm:compact-bijection-homeo}
A continuous bijection between compact Hausdorff spaces is a
homeomorphism.
\depends{Mathlib's \texttt{Continuous.homeoOfEquivCompactToT2}
or analogous topology fact (PRESENT).}
\lean{Continuous.homeoOfEquivCompactToT2}
\leanok\mathlibok
\end{theorem}
\begin{proof}\leanok\end{proof}

\begin{layman}
A purely topological gem: any continuous one-to-one onto map from one
compact Hausdorff space to another is automatically a homeomorphism —
its inverse is continuous for free, no extra checking required. The
reason is a chain of clean implications. Closed subsets of a compact
space are themselves compact. Compact subsets of a Hausdorff space are
closed. So the map sends closed sets to closed sets, which is exactly
continuity of the inverse. Why bother? Without it we'd have to manually
verify that the inverse is continuous everywhere, which on a curvy
surface is fiddly. With it, going from ``continuous bijection'' to
``isomorphism of topological spaces'' is one line. Mathlib already has
this packaged.
\end{layman}

\begin{theorem}[Classical input: Degree-one maps are isomorphisms (umbrella)]
\label{input:degree-one-isomorphism}
\uses{thm:degree-one-bijective,thm:local-biholo-unramified,thm:compact-bijection-homeo}
\leanok
A nonconstant holomorphic map \(f:X\to\CPone\) of degree one is a
biholomorphism.
\lean{JacobianChallenge.Blueprint.input_degree_one_isomorphism}
\end{theorem}
\begin{proof}\leanok\end{proof}

\begin{layman}
We package the chain ``degree-one nonconstant holomorphic map between
compact Riemann surfaces is a biholomorphism'' as a single classical
input. It bundles three steps: degree one means no ramification; no
ramification means a local biholomorphism everywhere; and a continuous
bijection between compact Hausdorff spaces is a homeomorphism — together
giving a global holomorphic isomorphism. Why bother? Combined with the
genus-zero existence proposition (genus zero gives a degree-one map to
the sphere), this umbrella delivers the forward direction of the
genus-zero classification: any genus-zero compact Riemann surface is
\emph{biholomorphic} to the Riemann sphere, hence in particular
homeomorphic to the topological sphere. That's the anti-hack
``genus zero iff homeomorphic to sphere'' baked into the challenge
statement.
\end{layman}

\begin{proof}[Proof of Theorem~\ref{thm:genus-zero-classification}]
If \(g(X)=0\), Proposition~\ref{prop:genus-zero-degree-one-map} and
Input~\ref{input:degree-one-isomorphism} identify \(X\) biholomorphically,
hence homeomorphically, with \(\CPone\), whose underlying topological space is
\(\Sphere\).

Conversely, if \(X\) is homeomorphic to \(\Sphere\), the topological genus is
zero. The comparison theorem between analytic genus
\(\dim_{\C}H^{0}(X,\Omega^{1}_{X})\) and topological genus gives \(g(X)=0\).
\end{proof}

\begin{formalizationnote}
The current Lean target splits this into the two directions in
\code{Jacobian/HolomorphicForms/GenusZeroClassification.lean}. The forward
direction needs Riemann-Roch, meromorphic functions, and degree-one map
classification. The reverse direction needs comparison of analytic and
topological genus.
\end{formalizationnote}

\subsection{Degree-one meromorphic-to-sphere classification: structural decomposition}
\label{sec:degree-one-mer-decomp}

The chain ``meromorphic map with pole divisor \([P]\) \(\Rightarrow\)
continuous \(\Rightarrow\) bijective'' factors into structural axioms
on the project's abstract \code{MeromorphicMapToSphere} interface,
since this interface does not yet expose the geometric content
linking the abstract \code{poleDivisor} to the concrete \code{toMap}.

\begin{lemma}[Continuity off the pole]
\label{lem:meromorphic-continuous-off-pole}
\uses{def:divisors-on-X}
A meromorphic map \(f:X\to\CPone\) with pole divisor \([P]\) is
continuous on \(X\setminus\{P\}\).
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.continuousOn_compl_pole_of_poleDivisor_point}
\end{lemma}
\begin{proof}
Off the pole locus, \(f\) takes only finite values. In any chart at
a finite point, \(f\) coincides with a smooth \(\CC\)-valued
function (the chart-local representative). Smoothness implies
continuity in the chart, and the inclusion \(\iota:\CC\to\CPone\) is
continuous. Hence \(f\) is continuous at every point of
\(X\setminus\{P\}\).
\end{proof}

\begin{lemma}[Tendency to \(\infty\) at a simple pole]
\label{lem:meromorphic-tends-to-infty-at-simple-pole}
\uses{def:divisors-on-X}
A meromorphic map \(f:X\to\CPone\) with pole divisor \([P]\) tends
to \(\infty\in\CPone\) along the neighbourhood filter at \(P\).
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.tendsto_infty_at_pole_of_poleDivisor_point}
\end{lemma}
\begin{proof}
In a chart at \(P\), the local representative of \(f\) is a
meromorphic function with a simple pole at the chart image of \(P\).
The local Laurent expansion takes the form
\(z\mapsto a/(z-z_{0})+\text{holomorphic}\) with \(a\neq 0\), which
diverges in modulus as \(z\to z_{0}\). The one-point topology on
\(\CPone\) translates modulus-divergence into convergence to
\(\infty\).
\end{proof}

\begin{lemma}[Value at a simple pole is \(\infty\)]
\label{lem:meromorphic-value-at-pole}
\uses{def:divisors-on-X}
A meromorphic map \(f:X\to\CPone\) with pole divisor \([P]\) has
\(f(P)=\infty\).
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.toMap\_pole\_eq\_infty\_of\_poleDivisor\_point}
\end{lemma}
\begin{proof}
The data of a meromorphic map records both the divisor and the
extended map. By construction, the extension assigns the value
\(\infty\) at every pole point. (At the project's interface level,
this is an axiomatic structural field that the eventual concrete
construction will discharge.)
\end{proof}

\begin{theorem}[Continuous extension over a simple pole]
\label{thm:meromorphic-continuous-extension}
\uses{lem:meromorphic-continuous-off-pole,lem:meromorphic-tends-to-infty-at-simple-pole,lem:meromorphic-value-at-pole}
A meromorphic map \(f:X\to\CPone\) with pole divisor \([P]\) on a
compact Riemann surface is continuous as a map \(X\to\CPone\).
\lean{JacobianChallenge.HolomorphicForms.meromorphicMapToSphere_continuous_of_poleDivisor_point}
\leanok
\end{theorem}
\begin{proof}\leanok
Continuity is local. At any point \(x\neq P\) use
Lemma~\ref{lem:meromorphic-continuous-off-pole}. At \(x=P\), the
limit characterisation of continuity reduces to
\(\lim_{x\to P}f(x)=f(P)\), which is
Lemma~\ref{lem:meromorphic-tends-to-infty-at-simple-pole} together
with Lemma~\ref{lem:meromorphic-value-at-pole}.
\end{proof}

\begin{lemma}[Surjectivity for degree-one continuous]
\label{lem:degree-one-surjective}
\uses{def:divisors-on-X}
A continuous meromorphic map \(f:X\to\CPone\) of pole-degree one is
surjective.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.surjective_of_continuous_and_pole_degree_one}
\end{lemma}
\begin{proof}
The image is compact (continuous image of a compact space) and
connected (continuous image of a connected space). Holomorphic maps
are open at every regular point; degree-one excludes ramification
entirely, so the map is open. The image is therefore a nonempty open
compact subset of the connected sphere, hence the whole sphere.
\end{proof}

\begin{lemma}[Injectivity for degree-one continuous]
\label{lem:degree-one-injective}
\uses{def:divisors-on-X}
A continuous meromorphic map \(f:X\to\CPone\) of pole-degree one is
injective.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.injective_of_continuous_and_pole_degree_one}
\end{lemma}
\begin{proof}
Pole-degree one means the map has degree one in the sense of
branched coverings. A degree-one map between compact connected
Riemann surfaces has a generic fiber of cardinality one; combined
with the no-ramification consequence of degree one, the fiber over
every point has cardinality one. Hence injectivity.
\end{proof}

\begin{theorem}[Degree-one bijectivity]
\label{thm:degree-one-bijectivity-meromorphic}
\uses{lem:degree-one-surjective,lem:degree-one-injective}
A continuous meromorphic map \(f:X\to\CPone\) of pole-degree one is
bijective.
\lean{JacobianChallenge.HolomorphicForms.meromorphicMapToSphere_bijective_of_poleDivisor_degree_one}
\leanok
\end{theorem}
\begin{proof}\leanok
Combine surjectivity (Lemma~\ref{lem:degree-one-surjective}) and
injectivity (Lemma~\ref{lem:degree-one-injective}).
\end{proof}

\subsection{Uniformization-lite: holomorphic 1-forms vanish on the topological sphere}
\label{sec:uniformization-lite}

\begin{lemma}[Holomorphic 1-form equivalence under sphere homeomorphism]
\label{lem:holomorphic-one-form-equiv-of-homeo-sphere}
\uses{def:holomorphic-one-form}
If a compact connected complex 1-manifold \(X\) is homeomorphic
(as a topological space) to the standard \(2\)-sphere, then there
is a \(\CC\)-linear equivalence
\(H^{0}(X,\Omega^{1}_{X})\cong H^{0}(\CPone,\Omega^{1}_{\CPone})\).
\lean{JacobianChallenge.HolomorphicForms.holomorphicOneForm_linearEquiv_of_homeoSphere_exists}
\end{lemma}
\begin{proof}
This is the genus-zero case of the uniformization theorem. Any
complex structure on the topological 2-sphere is biholomorphic to
the standard structure on \(\CPone=\OnePoint\,\CC\); the resulting
biholomorphism \(\psi:X\xrightarrow{\sim}\CPone\) pulls back
holomorphic 1-forms to holomorphic 1-forms, yielding the
\(\CC\)-linear isomorphism
\(\psi^{*}:H^{0}(\CPone,\Omega^{1}_{\CPone})\to H^{0}(X,\Omega^{1}_{X})\).
\end{proof}

\begin{theorem}[Holomorphic 1-forms vanish on the topological sphere]
\label{thm:homeo-sphere-holomorphic-one-form-vanishing}
\uses{lem:holomorphic-one-form-equiv-of-homeo-sphere}
A compact connected Riemann surface homeomorphic to the standard
\(2\)-sphere has \(\dim_{\CC}H^{0}(X,\Omega^{1}_{X})=0\); equivalently,
the space of holomorphic 1-forms is a subsingleton.
\lean{JacobianChallenge.HolomorphicForms.homeoSphereHolomorphicOneFormVanishing}
\leanok
\end{theorem}
\begin{proof}\leanok
By Lemma~\ref{lem:holomorphic-one-form-equiv-of-homeo-sphere}, the
holomorphic 1-form space on \(X\) is \(\CC\)-linearly isomorphic to
that on \(\CPone\). The latter is a subsingleton (it is in fact
zero, since \(\CPone\) has genus 0). Subsingleton transports
through linear equivalences, so \(H^{0}(X,\Omega^{1}_{X})\) is
itself a subsingleton.
\end{proof}

\subsection{Identity- and inversion-chart coefficient extraction}
\label{sec:chart-coeff-extraction}

\begin{lemma}[Identity-chart coefficient is \(C^{\infty}\)]
\label{lem:identity-chart-coeff-contdiff}
\uses{def:holomorphic-one-form}
For \(\omega\in H^{0}(\CPone,\Omega^{1}_{\CPone})\), the function
\(\CC\to\CC\) obtained by reading \(\omega\) in the identity chart
of \(\CPone\) and evaluating on \(1\in\CC\) is \(C^{\infty}\).
\lean{JacobianChallenge.HolomorphicForms.holomorphicOneFormIdentityChartCoeffContDiff}
\end{lemma}
\begin{proof}
The cotangent-bundle section \(\omega\) is smooth in any chart of
\(\CPone\). In the identity chart, the local representative is a
smooth section of the trivial cotangent bundle on \(\CC\), i.e.\ a
smooth covector field. Evaluating a smooth covector field on a
constant tangent vector yields a smooth scalar function. The
specific Mathlib gap is the \emph{chart-trivialisation API for
\code{ContMDiffSection}} on the cotangent bundle, which is absent
in v4.28.0 — once supplied, the proof is immediate.
\end{proof}

\begin{lemma}[Inversion-chart coefficient is continuous at \(0\)]
\label{lem:inversion-chart-coeff-continuous-at-zero}
\uses{def:holomorphic-one-form}
For \(\omega\in H^{0}(\CPone,\Omega^{1}_{\CPone})\), the function
\(\CC\to\CC\) obtained by reading \(\omega\) in the inversion chart
of \(\CPone\) and evaluating on \(1\in\CC\) is continuous at
\(0\in\CC\).
\lean{JacobianChallenge.HolomorphicForms.holomorphicOneFormInversionChartCoeffContinuousAtZero}
\end{lemma}
\begin{proof}
Identical to the proof of
Lemma~\ref{lem:identity-chart-coeff-contdiff}, applied in the
inversion chart in place of the identity chart. Same chart-
trivialisation Mathlib gap.
\end{proof}

\begin{lemma}[No-\(\infty\) off the pole locus]
\label{lem:meromorphic-no-infty-off-pole}
\uses{def:divisors-on-X}
A meromorphic map \(f:X\to\CPone\) with pole divisor \([P]\) takes
finite values off \(P\): \(\forall x\neq P,\ f(x)\neq\infty\).
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.toMap\_ne\_infty\_off\_pole}
\end{lemma}
\begin{proof}
The pole-divisor records the exact \(\infty\)-locus; pole divisor
\([P]\) means only \(P\) is sent to \(\infty\).
\end{proof}

\begin{lemma}[Continuity from no-\(\infty\)]
\label{lem:meromorphic-continuous-on-finite-set}
\uses{def:divisors-on-X}
On any subset \(S\subseteq X\) where \(f\) takes only finite values,
\(f:X\to\CPone\) is continuous on \(S\).
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.continuousOn\_of\_no\_infty\_on}
\end{lemma}
\begin{proof}
On \(S\), \(f\) factors through \(\iota:\CC\to\CPone\) via a smooth
\(g:S\to\CC\); both \(g\) and \(\iota\) are continuous, so the
composition is continuous on \(S\).
\end{proof}

\begin{lemma}[Modulus diverges at a simple pole]
\label{lem:simple-pole-modulus-diverges}
\uses{def:divisors-on-X}
For a meromorphic map \(f:X\to\CPone\) with \(\poles(f)=[P]\), there
exists a smooth \(\CC\)-valued lift \(g:X\setminus\{P\}\to\CC\)
satisfying \(f|_{X\setminus\{P\}}=\iota\circ g\) and
\(\|g(x)\|\to\infty\) as \(x\to P\).
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.modulus\_diverges\_at\_simple\_pole}
\end{lemma}
\begin{proof}
Off \(P\), use Lemma~\ref{lem:meromorphic-no-infty-off-pole} to
construct \(g\). Near \(P\), the local Laurent expansion of \(f\)
takes the form \(z\mapsto a/(z-z_{0})+\text{holomorphic}\) with
\(a\neq 0\) (simple pole), so \(\|g(z)\|\sim|a|/|z-z_{0}|\to\infty\).
\end{proof}

\begin{lemma}[Modulus divergence implies \(\OnePoint\)-tendsto-\(\infty\)]
\label{lem:onepoint-tendsto-infty-of-modulus-diverges}
A \(\CC\)-valued function whose modulus diverges along a punctured
neighbourhood of \(P\), lifted to \(\OnePoint\,\CC\) via the
canonical inclusion, tends to \(\infty\) at \(P\).
\lean{JacobianChallenge.HolomorphicForms.OnePoint.tendsto\_infty\_of\_modulus\_diverges}
\end{lemma}
\begin{proof}
The neighbourhood basis of \(\infty\) in \(\OnePoint\,\CC\) consists
of complements of bounded sets. Modulus divergence means every
bounded set is eventually avoided, hence the lifted function
eventually lies in any neighbourhood of \(\infty\).
\end{proof}

\begin{lemma}[No ramification at degree 1]
\label{lem:degree-one-no-ramification-detail}
\uses{def:divisors-on-X}
A pole-degree-1 meromorphic map has trivial ramification divisor:
the local degree at every point is exactly 1.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.no\_ramification\_of\_pole\_degree\_one}
\end{lemma}
\begin{proof}
Riemann--Hurwitz: \(2g(X)-2=\deg(f)(2g(\CPone)-2)+\deg(R)\), so
\(\deg(R)=2g(X)+2(\deg(f))(g(\CPone)-1)\). With \(\deg(f)=1\) and
\(g(\CPone)=0\), this gives \(\deg(R)=2g(X)-2\geq 0\), and with
\(\deg(f)=1\) every fibre is a single (unramified) point, so
\(\deg(R)=0\) and there is no ramification.
\end{proof}

\begin{lemma}[No ramification implies constant fibre cardinality]
\label{lem:no-ramification-fiber-card-constant}
A continuous meromorphic map without ramification on a compact
connected manifold has fibres all of the same cardinality.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.fiber\_card\_constant\_of\_no\_ramification}
\end{lemma}
\begin{proof}
Without ramification, the map is locally a covering map. On a
compact connected base, the covering map has a constant degree
(this is the standard local-global property of unbranched covers).
\end{proof}

\begin{lemma}[Compact image]
\label{lem:meromorphic-image-iscompact}
The image of a continuous map from a compact space is compact.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.image\_isCompact}
\leanok
\end{lemma}
\begin{proof}\leanok
Direct from \code{IsCompact.image} on \code{isCompact\_univ}.
\end{proof}

\begin{lemma}[Open map for degree-one maps]
\label{lem:degree-one-open-map}
\uses{def:divisors-on-X}
A continuous meromorphic map \(f:X\to\CPone\) of pole-degree one is
an open map.
\lean{JacobianChallenge.HolomorphicForms.MeromorphicMapToSphere.isOpenMap\_of\_pole\_degree\_one}
\end{lemma}
\begin{proof}
Holomorphic maps are open at every regular point. Degree one
excludes ramification entirely, so every point is regular.
\end{proof}

\begin{lemma}[Cotangent transition formula on the overlap]
\label{lem:cotangent-transition-formula}
\uses{def:holomorphic-one-form,lem:onepoint-cx-chart-overlap-derivative,lem:onepoint-cx-chart-overlap-pullback}
For \(\omega\in H^{0}(\CPone,\Omega^{1}_{\CPone})\), there is a
punctured neighbourhood of \(0\in\CC\) (in the inversion chart) on
which the identity-chart coefficient \(f\) and the inversion-chart
coefficient \(g\) of \(\omega\) are related by
\[
  f(w^{-1})=-w^{2}g(w),\qquad w\neq 0.
\]
\lean{JacobianChallenge.HolomorphicForms.holomorphicOneForm\_identityInversionTransition\_eventually}
\leanok
\end{lemma}
\begin{proof}\leanok
Pointwise from Lemma~\ref{lem:onepoint-cx-chart-overlap-pullback};
the eventually-quantifier on the punctured neighbourhood follows
via \code{filter\_upwards}.
\end{proof}

\begin{lemma}[Derivative of inverse on the chart overlap]
\label{lem:onepoint-cx-chart-overlap-derivative}
For \(w\neq 0\), \(\frac{d}{dw}(w^{-1})=-w^{-2}\).
\lean{JacobianChallenge.HolomorphicForms.onePointCx\_chart\_overlap\_derivative}
\leanok
\end{lemma}
\begin{proof}\leanok
Direct from Mathlib's \code{hasDerivAt\_inv} on \(w\neq 0\).
\end{proof}

\begin{lemma}[Cotangent pullback on the chart overlap]
\label{lem:onepoint-cx-chart-overlap-pullback}
\uses{def:holomorphic-one-form,lem:onepoint-cx-chart-overlap-derivative}
For \(\omega\in H^{0}(\CPone,\Omega^{1}_{\CPone})\) and \(w\neq 0\),
\(f(w^{-1})=-w^{2}g(w)\), where \(f\) and \(g\) are respectively the
identity-chart and inversion-chart coefficients.
\lean{JacobianChallenge.HolomorphicForms.holomorphicOneForm\_chartOverlap\_pullback}
\end{lemma}
\begin{proof}
Apply the chain rule for cotangent vectors under
\(z\leftrightarrow w=z^{-1}\):
\(f(z)\,dz=f(w^{-1})\,d(w^{-1})=-f(w^{-1})\,w^{-2}\,dw\). Equating
with \(g(w)\,dw\) yields the identity.
\end{proof}

\subsection{Sup-norm completeness decomposition (CompactRiemannSurface)}
\label{sec:sup-norm-completeness-decomp}

\begin{lemma}[Pointwise limit exists]
\label{lem:holomorphic-one-form-pointwise-limit-exists}
A sup-norm Cauchy sequence of holomorphic 1-forms on a compact
Riemann surface admits a pointwise limit at every point of \(X\).
\lean{JacobianChallenge.HolomorphicForms.holomorphicOneForm\_supNorm\_cauchySeq\_pointwise\_limit\_exists}
\end{lemma}
\begin{proof}
Sup-norm Cauchy implies pointwise Cauchy in each fiber
\(\mathrm{Cot}_x(X)\), which is a Banach space, so the pointwise limit
exists.
\end{proof}

\begin{lemma}[Continuity of the pointwise limit]
\label{lem:holomorphic-one-form-limit-continuous}
\uses{lem:holomorphic-one-form-pointwise-limit-exists}
The pointwise limit of a sup-norm Cauchy sequence of holomorphic
1-forms is continuous.
\lean{JacobianChallenge.HolomorphicForms.holomorphicOneForm\_supNorm\_cauchySeq\_limit\_continuous}
\end{lemma}
\begin{proof}
Sup-norm Cauchy convergence is uniform; the uniform limit of
continuous functions is continuous (\code{TendstoUniformly.continuous}).
\end{proof}

\begin{lemma}[Holomorphicity of the pointwise limit (Weierstrass)]
\label{lem:holomorphic-one-form-limit-holomorphic}
\uses{lem:holomorphic-one-form-pointwise-limit-exists}
The pointwise limit of a sup-norm Cauchy sequence of holomorphic
1-forms is holomorphic.
\lean{JacobianChallenge.HolomorphicForms.holomorphicOneForm\_supNorm\_cauchySeq\_limit\_holomorphic}
\end{lemma}
\begin{proof}
Classical Weierstrass convergence theorem: a uniform limit of
holomorphic functions is holomorphic, via Morera's theorem (closed
contour integrals vanish under uniform convergence) or
power-series-coefficient convergence (Cauchy estimates pass to the
limit). \textbf{Mathlib gap}: v4.28.0 lacks a Weierstrass-convergence
theorem for holomorphic functions or sections.
\end{proof>

\subsection{Uniformization-lite further decomposition}
\label{sec:uniformization-lite-iter3}

\begin{lemma}[Biholomorphism from sphere homeomorphism]
\label{lem:uniformization-genus-zero-biholomorphism}
A compact connected complex 1-manifold homeomorphic to \(S^2\) admits
a biholomorphism to \(\OnePoint\,\CC\).
\lean{JacobianChallenge.HolomorphicForms.exists\_biholomorphism\_to\_OnePointCx\_of\_homeoSphere}
\end{lemma}
\begin{proof}
Classical uniformisation at genus 0: any complex structure on the
topological 2-sphere is biholomorphically equivalent to the standard
one on \(\OnePoint\,\CC\). One way to see this is to combine the
Riemann mapping theorem with a removable-singularities argument: a
biholomorphism between a chart and a disc in \(\CC\) extends across
\(\infty\) to a global biholomorphism with \(\OnePoint\,\CC\).
\end{proof}

\begin{lemma}[Pullback of holomorphic 1-forms via biholomorphism]
\label{lem:holomorphic-one-form-pullback-via-biholo}
A homeomorphism \(e:X\to\OnePoint\,\CC\) that is biholomorphic
induces a \(\CC\)-linear isomorphism of holomorphic 1-form spaces,
\(e^{*}:H^{0}(\OnePoint\,\CC,\Omega^{1})\to H^{0}(X,\Omega^{1})\).
\lean{JacobianChallenge.HolomorphicForms.holomorphicOneForm\_linearEquiv\_of\_biholo\_to\_OnePointCx}
\end{lemma>
\begin{proof}
Standard pullback of forms via biholomorphism: \(e^*\omega(v):=\omega(de\cdot v)\)
is a cotangent-space pullback, \(\CC\)-linear in \(\omega\), and an
isomorphism because \(de\) is invertible at every point.
\end{proof}

\subsection{Chart-trivialisation API for ContMDiffSection}
\label{sec:chart-trivialisation-API}

\begin{lemma}[Identity-chart local representative is smooth]
\label{lem:section-localRepr-identity-chart-contdiff}
The cotangent-bundle section \(\omega.\code{toFun}\) pulled back through
\(\code{identityChart}.\code{symm}\) and evaluated at \(1:\CC\) gives a
\(C^{\infty}\) function on \(\CC\).
\lean{JacobianChallenge.HolomorphicForms.ContMDiffSection\_localRepr\_identityChart\_contDiff}
\end{lemma}
\begin{proof}
A \(\code{ContMDiffSection}\) is by definition smooth in any chart of
the bundle's base. In the identity chart of \(\OnePoint\,\CC\), the
local representative is a smooth section of the trivial cotangent
bundle on \(\CC\); evaluating on the constant tangent vector \(1\) is
a smooth (in fact \(\CC\)-linear) operation. \textbf{Mathlib gap}: a
chart-trivialisation API for \code{ContMDiffSection} on the cotangent
bundle is not in v4.28.0.
\end{proof}

\begin{lemma}[Inversion-chart local representative is continuous at zero]
\label{lem:section-localRepr-inversion-chart-continuous-at-zero}
The cotangent-bundle section pulled back through
\(\code{inversionChart}.\code{symm}\) and evaluated at \(1:\CC\) is
continuous at \(w=0\).
\lean{JacobianChallenge.HolomorphicForms.ContMDiffSection\_localRepr\_inversionChart\_continuousAt\_zero}
\end{lemma>
\begin{proof}
Same chart-trivialisation argument as
Lemma~\ref{lem:section-localRepr-identity-chart-contdiff}, applied
in the inversion chart instead.
\end{proof>

