\section{Complex Tori and the Jacobian}
\label{sec:complex-tori-jacobians}

\begin{layman}
A \emph{complex torus} is one of the cleanest objects in geometry.
Take a finite-dimensional complex vector space \(V\) — say
\(\mathbb{C}^g\). Pick a \emph{full lattice} \(\Lambda\) inside it:
a discrete grid of points whose integer combinations spread evenly
in every direction, like the vertices of a wallpaper pattern. Glue
the space to itself by declaring two vectors equivalent whenever
they differ by an element of \(\Lambda\). What remains is a
compact, smooth, complex manifold \(V/\Lambda\). In dimension one,
it is the surface of an ordinary doughnut. In higher dimension, it
is a higher-genus generalisation that retains every desirable
property: it adds (the addition descends from \(V\)), it's
Hausdorff and compact, it's a complex manifold, addition is smooth.
Every operation you might want is automatic.

This section packages those properties into a single
\emph{complex torus package} — a proposition that asserts, at
once, that \(V/\Lambda\) carries each of the structures the
challenge demands. The proof is a careful unwinding of a quotient:
the topology and group come from the quotient of an abelian
topological group; charts come from balls small enough to avoid
nonzero lattice translates; the smooth and complex structures
inherit through the chart maps. None of this is exotic, but the
project does need every piece in place before it can construct
the Jacobian.

The \emph{Jacobian} of a Riemann surface is then a particular
complex torus: take \(V = H^0(X,\Omega^1_X)^{\vee}\), the dual of
the holomorphic 1-forms; take \(\Lambda = \) the period lattice
built in the previous section; apply the package. The resulting
quotient is a compact complex Lie additive group of complex
dimension \(g(X)\). Every challenge property of the Jacobian
follows directly from the package; we don't have to prove
``\(\Jac(X)\) is compact'' or ``\(\Jac(X)\) is a manifold'' as
separate theorems. The structural facts come bundled.

Why bother? In Buzzard's challenge, the third anti-hack family of
theorems is precisely a list of structural assertions: ``\(\Jac\)
is a compact complex manifold,'' ``\(\Jac\) is a Lie additive
group,'' ``addition and negation are smooth.'' Without the
complex-torus package, each of these would have to be proved by
hand for the period-lattice quotient — a thousand-line excursion.
With it, they fall out of one application.
\end{layman}

Let \(V\) be a finite-dimensional complex vector space and \(\Lambda\subset V\)
a full lattice. Then \(V/\Lambda\) is a compact complex Lie additive group.
The quotient map is a local biholomorphism after restricting to sufficiently
small balls avoiding nonzero lattice translates.

\begin{proposition}[Complex torus package]
\label{prop:complex-torus-package}
The quotient \(V/\Lambda\) has an additive commutative group structure,
Hausdorff topology, compactness, complex charted-space structure, complex
manifold structure, and compatible Lie additive group structure.
\lean{JacobianChallenge.ComplexTorus.FullComplexLattice, JacobianChallenge.ComplexTorus.quotient, JacobianChallenge.ComplexTorus.quotient_addCommGroup, JacobianChallenge.ComplexTorus.quotient_topologicalSpace, JacobianChallenge.ComplexTorus.quotient_t2Space, JacobianChallenge.ComplexTorus.quotient_compactSpace}
\leanok
\end{proposition}

\begin{layman}
Take a finite-dimensional complex vector space \(V\) — a few copies of
the complex plane — and a \emph{full lattice} \(\Lambda\) inside it: a
discrete grid of points whose integer combinations spread out evenly in
every direction, like the vertices of a tiled wallpaper pattern in
real-dimension \(2g\). Glue the space to itself by declaring two points
equivalent whenever they differ by a lattice vector. The result is a
\emph{complex torus}: in dimension one, just the surface of an ordinary
donut; in higher dimension, a higher-genus generalization that's still
compact, smooth, and inherits an addition law from \(V\). The
proposition packages all the structural facts at once: addition
commutes, the topology is Hausdorff and compact, the smooth structure
makes it a complex manifold, and addition itself is smooth. (You can
think of the building blocks like a Lego set: snap together vector
space, group, topology, manifold, and Lie group.) Why bother? When the
Jacobian is built later as ``dual of holomorphic 1-forms modulo period
lattice,'' we just plug \(V = \HdualX\) and \(\Lambda = \) period
lattice into this proposition and inherit every structural property
the challenge's anti-hack theorems demand.
\end{layman}

\begin{proof}
\leanok
The group and topology are induced by the quotient of the additive topological
group \(V\). Closedness and discreteness of \(\Lambda\) give Hausdorffness and
local injectivity of the quotient map. A compact fundamental parallelepiped
covers \(V/\Lambda\), proving compactness. Local charts are obtained by
choosing a ball \(B(v,r)\) on which the quotient map is injective; transition
maps are translations in \(V\), hence holomorphic and smooth. Addition and
negation are induced from smooth maps on \(V\).
\end{proof}

\begin{proof}[Construction of Definition~\ref{def:analytic-jacobian}]\leanok
Apply Proposition~\ref{prop:complex-torus-package} to
\[
  V=\HdualX,\qquad \Lambda=\Pi_X(H_1(X,\Z)).
\]
The full-lattice condition is exactly Theorem~\ref{thm:period-lattice}. This
produces the Jacobian \(\Jac(X)\) with all structural instances required by
the challenge.
\end{proof}

\begin{formalizationnote}
Most complex torus infrastructure is already present in
\code{Jacobian/ComplexTorus}. The challenge-facing carrier uses a
basis-aligned model \(\operatorname{Fin}(g)\to\C\) and a universe bridge via
\code{ULift}. The informal proof treats this as transport along a chosen
linear equivalence \(\HdualX\cong\C^g\).
\end{formalizationnote}
