\section{Main Theorem Assembly}
\label{sec:main-assembly}

\begin{layman}
Every previous section has been constructive: each built one piece
of infrastructure that the challenge demands. This section is the
moment of assembly. We take the analytic genus from section 2, the
period lattice from section 6, the complex-torus package from
section 7, the Abel--Jacobi map from section 8, and the trace
identity from section 9, and we plug them, one at a time, into
the slots demanded by \code{Jacobian/Challenge.lean}.

What does ``the slots'' mean? The challenge file declares about
two dozen named definitions and theorems with literal \code{sorry}
placeholders. \code{genus X} is a slot: it must be a natural
number. \code{Jacobian X} is a slot: it must be a type carrying
addition, topology, compactness, smoothness, complex structure,
Lie group structure. \code{ofCurve P} is a slot: a holomorphic
map from \(X\) to its Jacobian. \code{ofCurve_inj} is a slot:
the proof that this map is injective in positive genus.
\code{pushforward}, \code{pullback}, \code{degree}, and
\code{pushforward_pullback} are further slots, demanding the
trace identity of section 9. Each slot is filled by pointing
at the corresponding theorem of the previous sections.

Slot-filling sounds mechanical, but it has subtleties. The
challenge wants \code{Jacobian X} to be a particular kind of
algebraic-topological gadget — an additive abelian group with
extra structure — and the analytic construction produces a
quotient of a vector space by a lattice, which is a different
formal object until we transport along the right equivalences.
The Lean side handles these transports via the
\emph{basis-aligned} model that picks an explicit isomorphism
\(H^0(X,\Omega^1_X)^{\vee} \cong \mathbb{C}^{g(X)}\) and runs the
construction on the standard \(\mathbb{C}^g\) carrier. The
informal proof here is silent about the bookkeeping and focuses
on the mathematical content of each slot.

When this section's single theorem is fully discharged in Lean,
the entire challenge is met.
\end{layman}

We now assemble the declarations required by \code{Jacobian/Challenge.lean}.

\begin{theorem}[Challenge API from the analytic construction]
\label{thm:challenge-api}
\uses{thm:fd-holomorphic-one-forms,thm:genus-zero-classification,def:analytic-jacobian,def:abel-jacobi,lem:aj-self,lem:aj-holomorphic,thm:abel-jacobi-injective,thm:push-pull-functoriality,thm:pushforward-pullback}
The analytic period-lattice construction supplies all definitions and theorems
in the Jacobian Challenge API.
\lean{genus, genus_eq_zero_iff_homeo, Jacobian, Jacobian.ofCurve, Jacobian.pushforward, Jacobian.pullback, Jacobian.pushforward_pullback}
\leanok
\end{theorem}

\begin{layman}
This is the moment all the bookkeeping pays off. We assemble the public
API of the Jacobian Challenge — the small set of definitions and
theorems that \texttt{Jacobian/Challenge.lean} exposes — directly from
the analytic period-lattice construction. \emph{Genus} is the
finite-dimensional dimension of holomorphic 1-forms; the genus-zero
classification matches it to the topological sphere. The
\emph{Jacobian} is the dual-of-1-forms quotient by the period lattice,
inheriting all its algebraic, topological, and analytic structure from
the complex-torus package. \emph{Abel–Jacobi} is the path-integration
map, holomorphic and (in positive genus) injective. \emph{Pullback}
and \emph{pushforward} between Jacobians come from the dual of the
1-form maps, and the trace identity gives the key
``push-then-pull equals multiplication-by-degree'' equation. Why
bother? This is the deliverable. Once every constituent theorem is
formally proved in Lean, this assembly node certifies that the entire
\texttt{Challenge.lean} API holds — finishing the challenge.
\end{layman}

\begin{proof}
Define \code{genus X} to be the analytic genus
\(\dim_{\C}H^{0}(X,\Omega^{1}_{X})\). Theorem~\ref{thm:fd-holomorphic-one-forms}
ensures this dimension is finite, and Theorem~\ref{thm:genus-zero-classification}
proves \code{genus_eq_zero_iff_homeo}.

Define \code{Jacobian X} to be the complex torus
\(\HdualX/\periods_X\). Theorem~\ref{thm:period-lattice} makes
\(\periods_X\) a full lattice, and Proposition~\ref{prop:complex-torus-package}
gives the additive group, topology, Hausdorffness, compactness, charted-space,
manifold, and Lie additive group structures.

Define \code{Jacobian.ofCurve P} to be \(\AJ_P\). Lemma~\ref{lem:aj-self}
proves \code{ofCurve_self}; Lemma~\ref{lem:aj-holomorphic} proves
\code{ofCurve_contMDiff}; Theorem~\ref{thm:abel-jacobi-injective} proves
\code{ofCurve_inj}.

For a holomorphic map \(f:X\to Y\), define \code{ContMDiff.degree f hf} as
the analytic degree. Define \code{Jacobian.pullback f hf} and
\code{Jacobian.pushforward f hf} by the descended maps from
Lemma~\ref{lem:push-pull-descend}. The holomorphicity, identity, and
composition laws are Theorem~\ref{thm:push-pull-functoriality}.

Finally, \code{pushforward_pullback} is exactly
Theorem~\ref{thm:pushforward-pullback}.
\end{proof}
